---
title: "Optimization of video monitoring for reef fish assessments"
author: "Stijn bruneel"
date: "20 November 2019"
output:
  pdf_document: default
  word_document: default
fig_caption: yes
---

```{r global_options, include=FALSE}
# knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```

```{r warning=FALSE, message=FALSE, include=FALSE}
#Different useful library, not all of them are being used here
library(readxl)
library(rlang)
library(wrapr)
library(dplyr)
library(ggplot2)
library(nlme)
library(lme4)
library(arm)
library(mgcv)
library(lmerTest)
library(MuMIn)
library(DAAG)
library(vegan)
library(tibble)
library(pvclust)
library(cluster)
library(vegan)
library(reshape2)
library(diverse)
library(labdsv)
library(DataCombine)
library(reshape2)
library(tibble)
library(plotly)
library(slam)
library(qlcMatrix)
library(popbio)
library(indicspecies)
library(iterators)
library(parallel)
library(foreach)
library(doParallel)
library(knitr)
library(gridExtra)
library(readxl)
library(ggpubr)
library(ggplot2)
library(scales) # for "comma"
library(magrittr)
library(sp)
library(leaflet)
library(glmmADMB)
library(glmmTMB)
library(sjstats)
library(flextable)
library(kableExtra)
library(data.table)
library(DHARMa)
```

```{r}
if (file.exists("./combinations/")==FALSE){dir.create("./combinations/")}
if (file.exists("./Rdata/")==FALSE){dir.create("./Rdata/")}
```

```{r echo=FALSE}
#Read and process the list with observed species. This file will be used later to select the 'species' columns from the data 
specieslist=read_excel("./specieslist_fake.xlsx")
specieslist=as.data.frame(specieslist[,2])
colnames(specieslist)="Species"
specieslist<-t(specieslist)
colnames(specieslist)<-specieslist
```

```{r echo=FALSE}
# Preprocess the data of your choice
preprocess_data<-function(file_name){
  data <- read_excel(file_name)
  data$Code<-paste(data$Location,data$Transect,data$Person)
  data$loctranspers<-paste(data$Location,data$Transect,data$Repeat)
  data$Code_direction<-paste(data$Code,data$direction,sep="_")
  data$Island<-substr(data$Location,1,1)
  data$Island[which(data$Island=="B")]<-"SantaCruz"
  data$Island[which(data$Island=="C")]<-"Floreana"
  data$Code_Transect<-paste(data$Location,data$Transect,sep="_")
  data$Location_Transect_direction<-paste(data$Code_Transect,data$direction,sep="_")
  return(data)
}
```

```{r echo=FALSE}
#In data sets of different transect lengths, different species might be present. For example a species seen during 50 meter transects might not have been seen in the 10 meter transects. Tis species is then added to the 10 meter data frame as an empty column.
add_all_species<-function(data,specieslist){
  columns_to_insert=colnames(specieslist)[which(!(colnames(specieslist) %in% colnames(data)))]
  data[columns_to_insert]=0
  return(data)
}
```

```{r}
#Insert empty rows in case omitted. This makes sure that all data sets of different transect lengths have the same number of rows.
Insert.empty.rows<-function(data.repeat.100,data.repeat.300){
  if (abs(nrow(data.repeat.300)-nrow(data.repeat.100))>0){
    store=NA
    right.order<-colnames(data.repeat.300)
    data.repeat.100<-data.repeat.100[right.order]
    for (k in 1:(nrow(data.repeat.300)-nrow(data.repeat.100))){
      temp.vector<-which(data.repeat.100$Repeat!=data.repeat.300$Repeat)
      store[k]=temp.vector[1]
      data.repeat.100=InsertRow(data.repeat.100,data.repeat.300[temp.vector[1],],temp.vector[1]) 
      data.repeat.100[temp.vector[1],c(which(colnames(data.repeat.100) %in% colnames(specieslist)))]<-0
    }
    store.not.1<-store[which(data.repeat.100[store,"Repeat"]!=1)]
    store.1<-store[which(data.repeat.100[store,"Repeat"]==1)]
    
    data.repeat.100[store.not.1,]=data.repeat.100[store.not.1-1,]
    for (i in 1:length(store.not.1)){
      data.repeat.100[store.not.1[i],"Repeat"]=as.character(as.numeric(data.repeat.100[store.not.1[i],"Repeat"])+1)
    }
    
    if (length(store.1)>0){
      data.repeat.100[store.1,]=data.repeat.100[store.1+1,]
      for (i in 1:length(store.1)){
        data.repeat.100[store.1[i],"Repeat"]=as.character(as.numeric(data.repeat.100[store.1[i],"Repeat"])-1)
      }
    }
    
    data.repeat.100[store,"direction"]=data.repeat.100[store,"direction"]*(-1)
    data.repeat.100[store,c(which(colnames(data.repeat.100) %in% colnames(specieslist)))]=0
  }
  return(data.repeat.100)
}
```

```{r}
#Determine cumulative amount of species
Cum.species<-function(data,grouping){
  data$CumulativeamountofspeciesRepeat<-NA
    #Determine cumulative amount of species of repeats
    splitted_data<-split(data,f=lapply(data[,grouping],as.character)[[1]])
    for (i in 1:length(unique(lapply(data[,grouping],as.character)[[1]]))){
      x=splitted_data[[i]][,c(which(colnames(splitted_data[[i]]) %in% colnames(specieslist)))]
      for (j in 1:nrow(x)){
        y=x[c(1:j),]
        z=apply(y,2,function(z) {any(is.na(z)==FALSE)})
        cum=length(which(z==TRUE))
        newname1=paste('CumulativeamountofspeciesRepeat',grouping,sep="_")
        splitted_data[[i]][j,c(newname1)]=cum
        splitted_data[[i]]['CodeTransectRepeat']=1:nrow(splitted_data[[i]])
      }
      for (j in 1:nrow(x)){
        newname2=paste('CumulativeamountofspeciesRepeat',grouping,"standard",sep="_")
  splitted_data[[i]][j,c(newname2)]=splitted_data[[i]][j,c(newname1)]/splitted_data[[i]][nrow(splitted_data[[i]]),c(newname1)]
      }
    }
  data.repeat<- do.call("rbind", splitted_data)
  return(data.repeat)
}
```

```{r}
#The data set with the longest transect length will have the maximum number of rows and is therefore used as baseline to standaridze the other data sets.
RUN.baseline<-function(file_name){
  data<-preprocess_data(file_name)
  data<-add_all_species(data,specieslist)
}
#This is run for all data sets but the baseline, when the baseline is established.
RUN<-function(file_name,baseline){
  data<-preprocess_data(file_name)
  data<-add_all_species(data,specieslist)
  data<-Insert.empty.rows(data,baseline)
}
```

```{r}
#Preprocess the data, add all species and insert empty rows if needed
data.repeat.50<-RUN.baseline("./Data/Fake_data/N50.xlsx")
data.repeat.40<-RUN("./Data/Fake_data/N40.xlsx",data.repeat.50)
data.repeat.30<-RUN("./Data/Fake_data/N30.xlsx",data.repeat.50)
data.repeat.20<-RUN("./Data/Fake_data/N20.xlsx",data.repeat.50)
data.repeat.10<-RUN("./Data/Fake_data/N10.xlsx",data.repeat.50)
```

```{r}
#Cumulative species richness is determined for every observation using different grouping factors 
data.repeat.10<-Cum.species(data.repeat.10,"Code")
data.repeat.10<-Cum.species(data.repeat.10,"Code_Transect")
data.repeat.20<-Cum.species(data.repeat.20,"Code")
data.repeat.20<-Cum.species(data.repeat.20,"Code_Transect")
data.repeat.30<-Cum.species(data.repeat.30,"Code")
data.repeat.30<-Cum.species(data.repeat.30,"Code_Transect")
data.repeat.40<-Cum.species(data.repeat.40,"Code")
data.repeat.40<-Cum.species(data.repeat.40,"Code_Transect")
data.repeat.50<-Cum.species(data.repeat.50,"Code")
data.repeat.50<-Cum.species(data.repeat.50,"Code_Transect")
```

```{r echo=FALSE}
# Shannon index function based on vector data
SW<-function(row,data.repeat){
  row<-row[c(which(colnames(data.repeat) %in% colnames(specieslist)))]
  row<-row[which(is.na(row)==FALSE & row!=0)]
  numberofspecies=length(row)
  if (numberofspecies==0){
    H=0
  }
  if (numberofspecies!=0){
    som=sum(row)
    row<-row/som
    H<-(-1)*sum(row*log(row))
  }
  return(H)
}
# Run the Shannon index function and combine the outcome in the dataframe as an extra column
RUN.SW<-function(data.repeat){
  data.repeat$H<-NA
  for (i in 1:nrow(data.repeat)){
    H<-SW(data.repeat[i,],data.repeat)
    data.repeat$H[i]<-H
  }
  return(data.repeat)
}
data.repeat.10<-RUN.SW(data.repeat.10)
data.repeat.20<-RUN.SW(data.repeat.20)
data.repeat.30<-RUN.SW(data.repeat.30)
data.repeat.40<-RUN.SW(data.repeat.40)
data.repeat.50<-RUN.SW(data.repeat.50)
data.repeat<-data.repeat.50
```

```{r echo=FALSE}
#Transform the biological data of the data frame
Transformation_data<-function(x,type){
  #Select only the biological data
  x=x[,c(which(colnames(x) %in% colnames(specieslist)))]
  #Set all missing data to 0 (=absence)
  x[is.na(x)==TRUE]=0
  #Define the type of transformation
  if (type=="4root"){
    x<-sqrt(sqrt(x))
  }
  if (type=="no transformation"){
    x<-x
  }
  if (type=="log"){
    x<-log(x+1)
  }
  if (type=="log10"){
    x<-log10(x+1)
  }
  if (type=="presence-absence"){
     x[x>0] <-1
  }
  return(x)
}
```

```{r}
#Plot the cumulative number of species
g<-ggplot(data.repeat,aes(x=CodeTransectRepeat,y=CumulativeamountofspeciesRepeat_Code_Transect,group=Code_Transect))
  g <- g + geom_line(aes(colour=Location),alpha=0.3,lwd=2)
  g <- g + coord_cartesian(ylim = c(0, 30))
  g <- g + geom_point(pch=21,size=2) + ylab("Cumulative species richness")
g
```

```{r}
#Plot the normalized cumulative number of species
g<-ggplot(data.repeat,aes(x=CodeTransectRepeat,y=CumulativeamountofspeciesRepeat_Code_Transect_standard,group=Code_Transect))
  g <- g + geom_line(aes(colour=Location),alpha=0.3,lwd=2)
  g <- g + coord_cartesian(ylim = c(0, 1))
  g <- g + geom_point(pch=21,size=2) + ylab("Cumulative species richness")
g
```

```{r echo=FALSE}
data.repeat.temp<-data.repeat %>%
  dplyr::group_by(Repeat) %>%
  dplyr::summarize(mean_H=mean(H,na.rm=TRUE),
                   mean_richness=mean(CumulativeamountofspeciesRepeat_Code,na.rm=TRUE),
                   sd_richness=sd(CumulativeamountofspeciesRepeat_Code,na.rm = TRUE),
                   sd_H=sd(H,na.rm = TRUE)
                   )
n=540/6
data.repeat.temp$low_conf_mean<-data.repeat.temp$mean_richness-qt(0.975,df=n-1)*data.repeat.temp$sd_richness/sqrt(n)
data.repeat.temp$high_conf_mean<-data.repeat.temp$mean_richness+qt(0.975,df=n-1)*data.repeat.temp$sd_richness/sqrt(n)
#Plot the average cumulative number of species with confidence interval
g<-ggplot(data=data.repeat.temp,aes(x=Repeat,y=mean_richness,group=1))
g<-g+geom_line()+geom_point()
g<-g+geom_ribbon(data=data.repeat.temp,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean),alpha=0.2)
g
```

```{r echo=FALSE}
data.repeat.temp<-data.repeat %>%
  dplyr::group_by(CodeTransectRepeat) %>%
  dplyr::summarize(mean_H=mean(H,na.rm=TRUE),
                   mean_richness=mean(CumulativeamountofspeciesRepeat_Code_Transect,na.rm=TRUE),
                   sd_richness=sd(CumulativeamountofspeciesRepeat_Code_Transect,na.rm = TRUE),
                   sd_H=sd(H,na.rm = TRUE)
                   )
n=540/18
data.repeat.temp$low_conf_mean<-data.repeat.temp$mean_richness-qt(0.975,df=n-1)*data.repeat.temp$sd_richness/sqrt(n)
data.repeat.temp$high_conf_mean<-data.repeat.temp$mean_richness+qt(0.975,df=n-1)*data.repeat.temp$sd_richness/sqrt(n)
g<-ggplot(data=data.repeat.temp,aes(x=CodeTransectRepeat,y=mean_richness,group=1))
g<-g+geom_line()+geom_point()
g<-g+geom_ribbon(data=data.repeat.temp,aes(x=CodeTransectRepeat,ymin=low_conf_mean,ymax=high_conf_mean),alpha=0.2)
g
```

```{r echo=FALSE}
data.repeat.temp<-data.repeat %>%
  dplyr::group_by(CodeTransectRepeat) %>%
  dplyr::summarize(mean_H=mean(H,na.rm=TRUE),
                   mean_richness=mean(CumulativeamountofspeciesRepeat_Code_Transect_standard,na.rm=TRUE),
                   sd_richness=sd(CumulativeamountofspeciesRepeat_Code_Transect_standard,na.rm = TRUE),
                   sd_H=sd(H,na.rm = TRUE)
                   )
n=540/18
data.repeat.temp$low_conf_mean<-data.repeat.temp$mean_richness-qt(0.975,df=n-1)*data.repeat.temp$sd_richness/sqrt(n)
data.repeat.temp$high_conf_mean<-data.repeat.temp$mean_richness+qt(0.975,df=n-1)*data.repeat.temp$sd_richness/sqrt(n)
#Plot the normalized average cumulative number of species with confidence interval
g<-ggplot(data=data.repeat.temp,aes(x=CodeTransectRepeat,y=mean_richness,group=1))
g<-g+geom_line()+geom_point()
g<-g+geom_ribbon(data=data.repeat.temp,aes(x=CodeTransectRepeat,ymin=low_conf_mean,ymax=high_conf_mean),alpha=0.2)
g
```

```{r}
#Permutation-based SAC (Species Accumulation Curve)
SCA_Personal<-function(data.repeat,group,run){
  if (run=="YES"){
    runloop<-unique(data.repeat[,group])
    dim1=nrow(data.repeat)
    dim3=3
    numberofrepeats=dim1/nrow(runloop)
    SCA <- expand.grid(repeats=c(1:numberofrepeats),group=lapply(runloop,as.character)[[1]],stringsAsFactors = FALSE)
    SCA[,c("mean.S","upper.S","lower.S")]=NA
    for (i in 1:nrow(runloop)){
      BC=data.repeat[which(data.repeat[,group]==as.character(runloop[i,1])),]
      BC.fish<-Transformation_data(BC,"no transformation")
      S = apply( (BC.fish > 0), MARGIN = 1, FUN = sum)
      N = dim(BC.fish)[1]
      index = 1:N
      nperm = 10
      S.subset = matrix(rep(0,nperm*N),nrow = nperm, ncol = N)
      S.subset[1:nperm,N] = sum(apply( (BC.fish > 0), MARGIN = 2, FUN = sum) != 0 ) 
      for (iperm in 1:nperm) {
        for (isamp in 1:(N-1)) {             # for each sample size
          indexperm = sample(index, size = isamp, replace = F )   # get a random subset without replacement
          subset = BC.fish[indexperm,]
          S.subset[iperm,isamp] = sum(apply( (subset > 0), MARGIN = 2, FUN = sum) != 0 )
        }
      }
      quant.upper = function(x) quantile(x, prob = 0.975, na.rm = TRUE, digits=6)
      quant.lower = function(x) quantile(x, prob = 0.025, na.rm = TRUE, digits=6)
      var=colMeans(S.subset)
      SCA$mean.S[which(SCA$group==as.character(runloop[i,1]))] = var
      SCA$upper.S[which(SCA$group==as.character(runloop[i,1]))] = var+apply(S.subset,MARGIN = 2,sd)*qt(0.975,df=length(var)-1)
      SCA$lower.S[which(SCA$group==as.character(runloop[i,1]))] = var-apply(S.subset,MARGIN = 2,sd)*qt(0.975,df=length(var)-1)
    }
    return(SCA)
  }
}
```

```{r}
#Plot the SCA
SCA.plot<-function(SCA,xlim,ylim,annote){
  h<-ggplot(data = SCA,aes(x=repeats,y=mean.S,group=group))
  h<-h+xlim(0,xlim)+ylim(0,ylim)+ylab("Species richness")+xlab("Cumulative number of repeats")
  h<-h+geom_point(aes(color=group))+geom_line(aes(color=group))
  h<-h+geom_errorbar(data=SCA,aes(x=repeats,ymin=lower.S,ymax=upper.S),alpha=0.2)
  h<-h+theme(legend.position="none",
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))
  h<-h+annotate("text", x=xlim, y=ylim, label= annote ,size=8,family="serif")
  print(h)
  return(h)
}
#Plot the SCA
SCA.plot.different.colors.for.the.islands<-function(SCA,xlim,ylim,annote){
  h<-ggplot(data = SCA,aes(x=repeats,y=mean.S,group=group))
  h<-h+xlim(0,xlim)+ylim(0,ylim)+ylab("Species richness")+xlab("Cumulative number of repeats")
  h<-h+geom_point(aes(color=group))#+geom_line(aes(color=group))
  h<-h+geom_errorbar(data=SCA,aes(x=repeats,ymin=lower.S,ymax=upper.S),alpha=0.2)
  h<-h+theme(legend.text=element_text(size=12),
                           legend.justification=c(0.5,0.5),legend.key.size =  unit(0.3, "in"),
                           legend.position=c(0.90, 0.42),legend.title = element_blank(),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))
  h<-h+annotate("text", x=xlim, y=ylim, label= annote ,size=8,family="serif")
  print(h)
  return(h)
}
```

```{r}
#Determine and plot SCA
SCA_Transect<-SCA_Personal(data.repeat,"Code_Transect",run="YES")
h1<-SCA.plot(SCA_Transect,20,30,"(A)")
SCA_Location<-SCA_Personal(data.repeat,"Location",run="YES")
h2<-SCA.plot(SCA_Location,60,30,"(B)")
```

```{r}
#Turn strings into factors for model development
data.repeat.50$fIsland<-as.factor(data.repeat.50$Island)
data.repeat.50$fLocation<-as.factor(data.repeat.50$Location)
data.repeat.50$fCode_Transect<-as.factor(data.repeat.50$Code_Transect)
data.repeat.50$fPerson<-as.factor(data.repeat.50$Person)
data.repeat.50[is.na(data.repeat.50)==TRUE]=0
```


```{r echo=FALSE, warning=FALSE}
# Mixed model -------------------------------------------------------------
library(lme4)
library(lsmeans)

#Island: fixed, Location and Transect: nested random factors, Observer: crossed random factor
form.S<-as.formula(totalamountofspecies ~ Island           
                 + (1|Location/Code_Transect)
                 + (1|Person)
                 + (1|Person:Location) 
                 + (1|Person:Code_Transect)
                 )


M1.50.S<-lmer(form.S,data.repeat.50)
summary(M1.50.S)
icc(M1.50.S)

form.H<-as.formula(H ~ Island           
                 + (1|Location/Code_Transect)
                 + (1|Person)
                 + (1|Person:Location) 
                 + (1|Person:Code_Transect)
                 )

M1.50.H <- lmer(form.H, data.repeat.50)
```


```{r}
data.repeat.50$fLocation<-as.factor(data.repeat.50$Location)
for (i in specieslist){
  print(ggplot(aes_string(x = "fLocation", y = i),data=data.repeat.50)+geom_boxplot())
}
```

```{r}
#Create uniform plots
clean_theme<-theme(legend.title=element_text(size=5), legend.text=element_text(size=5),
                           legend.justification=c(0.5,0.5),legend.key.size =  unit(0.1, "in"),
                           #legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))
```


```{r}
#Determine order of observations to check for temporal autocorrelation
autocorrelation_check_data=read_excel("./autocorrelation_check.xlsx")
data_full_autocorr=data.repeat.50
```

```{r}
#Check how many unique values are to be found per column of a dataframe
totaluniquevals <- function(df) {
  x <<- data.frame("Row Name"= numeric(0), "TotalUnique"=numeric(0), "IsNA"=numeric(0))
  result <- sapply(df, function(x) length(unique(x)))
  isnatotals <- sapply(df, function(x) sum(is.na(x)))

  #Now Create the Row names
  for (i in 1:length(colnames(df))) {
    x[i,1] <<- (names(result[i]))
    x[i,2] <<- result[[i]]
    x[i,3] <<- isnatotals[[i]]

  }
  return(x)
}
```

```{r}
#Binomial model for series of 18 repeats
data_full_autocorr_merged_bin=merge(data_full_autocorr,autocorrelation_check_data,by=c("Location","Transect","Person","Repeat"))
data_full_autocorr_merged_bin_biol=Transformation_data(data_full_autocorr_merged_bin,type="presence-absence")
data_full_autocorr_merged_bin_biol$Location=data_full_autocorr_merged_bin$Location
data_full_autocorr_merged_bin_biol$Transect=data_full_autocorr_merged_bin$Transect
data_full_autocorr_merged_bin_biol$Order=data_full_autocorr_merged_bin$Order
data_full_autocorr_merged_bin_biol$Code_Transect=paste(data_full_autocorr_merged_bin_biol$Location,data_full_autocorr_merged_bin_biol$Transect)
data_full_autocorr_merged_bin_biol$Person<-data_full_autocorr_merged_bin$Person
data_full_autocorr_merged_bin_biol$fOrder=as.factor(data_full_autocorr_merged_bin_biol$Order)
data_full_autocorr_merged_bin_biol$Island<-data_full_autocorr_merged_bin$Island
data_full_autocorr_merged_bin_biol<-data_full_autocorr_merged_bin_biol[order(data_full_autocorr_merged_bin_biol$Location,data_full_autocorr_merged_bin_biol$Transect,data_full_autocorr_merged_bin_biol$Order),]

a=Transformation_data(data_full_autocorr_merged_bin_biol,type="no transformation")
y=totaluniquevals(a)

specieslist.SC<-specieslist[which(specieslist %in% y$Row.Name[which(y$TotalUnique==2)])]
specieslist.SC<-specieslist

stringToQuoser <- function(varName) {
  wrapr::let(c(VARNAME = varName), quo(VARNAME))
}

for (j in 1:length(specieslist.SC)){
  response <- stringToQuoser(specieslist.SC[j])
  data_full_autocorr_merged_bin_biol_detected<-data_full_autocorr_merged_bin_biol %>%
    dplyr::group_by(Code_Transect) %>%
    dplyr::summarize(presence=sum((!!response)))
  data_full_autocorr_merged_bin_biol_for_model=data_full_autocorr_merged_bin_biol[which(data_full_autocorr_merged_bin_biol$Code_Transect %in% data_full_autocorr_merged_bin_biol_detected$Code_Transect[which(data_full_autocorr_merged_bin_biol_detected$presence!=0)]),]
  if (length(which(data_full_autocorr_merged_bin_biol_detected$presence!=0))>1){
    mbin=glmer(as.formula(paste(specieslist.SC[j],"~1+Order+(1|Code_Transect)")), data = data_full_autocorr_merged_bin_biol_for_model, family = binomial)} else {mbin=glm(as.formula(paste(specieslist.SC[j],"~1+Order")), data = data_full_autocorr_merged_bin_biol_for_model, family = binomial)}
  print(summary(mbin))
  r=as.data.frame(summary(mbin)$coefficients)
  rownames(r)[1]=specieslist.SC[j]
  if (j==1){
    p=r
  } else {p=rbind(p,r)}
  data_full_autocorr_merged_bin_biol_for_graph<-data_full_autocorr_merged_bin_biol_for_model[,c(specieslist.SC[j],"Order","Code_Transect")]
  data_full_autocorr_merged_bin_biol_for_graph[,specieslist.SC[j]]=as.factor(data_full_autocorr_merged_bin_biol_for_graph[,specieslist.SC[j]])
  data_full_autocorr_merged_bin_biol_for_graph[,"Code_Transect"]=as.factor(data_full_autocorr_merged_bin_biol_for_graph[,"Code_Transect"])
  g1<-ggplot(data=data_full_autocorr_merged_bin_biol_for_graph,aes_string(x="Order",y=specieslist.SC[j]))+clean_theme()+geom_point(position=position_jitter(w = 0, h = 0.2),aes_string(color="Code_Transect",shape=specieslist.SC[j]))+theme(legend.position = "none")+clean_theme+ggtitle(specieslist.SC[j])
  #Plot presence and absence in function of ordered repeat with different colors for different transects
 print(g1)
}
p[,c("Estimate","Std. Error","z value")]=round(p[,c("Estimate","Std. Error","z value")],digits = 2)
p[,c("Pr(>|z|)")]=round(p[,c("Pr(>|z|)")],digits = 6)
```

```{r}
#Binomial model for series of 6 repeats
data_full_autocorr_merged_bin=merge(data_full_autocorr,autocorrelation_check_data,by=c("Location","Transect","Person","Repeat"))
data_full_autocorr_merged_bin_biol=Transformation_data(data_full_autocorr_merged_bin,type="presence-absence")
data_full_autocorr_merged_bin_biol$Location=data_full_autocorr_merged_bin$Location
data_full_autocorr_merged_bin_biol$Transect=data_full_autocorr_merged_bin$Transect
data_full_autocorr_merged_bin_biol$Order=data_full_autocorr_merged_bin$Order
data_full_autocorr_merged_bin_biol$Code_Transect=paste(data_full_autocorr_merged_bin_biol$Location,data_full_autocorr_merged_bin_biol$Transect)
data_full_autocorr_merged_bin_biol$Person<-data_full_autocorr_merged_bin$Person
data_full_autocorr_merged_bin_biol$fOrder=as.factor(data_full_autocorr_merged_bin_biol$Order)
data_full_autocorr_merged_bin_biol$Island<-data_full_autocorr_merged_bin$Island
data_full_autocorr_merged_bin_biol$Repeat<-as.numeric(data_full_autocorr_merged_bin$Repeat)
data_full_autocorr_merged_bin_biol$Code_Transect_Person<-paste(data_full_autocorr_merged_bin$Code_Transect,data_full_autocorr_merged_bin$Person)
data_full_autocorr_merged_bin_biol<-data_full_autocorr_merged_bin_biol[order(data_full_autocorr_merged_bin_biol$Location,data_full_autocorr_merged_bin_biol$Transect,data_full_autocorr_merged_bin_biol$Person,data_full_autocorr_merged_bin_biol$Repeat),]

a=Transformation_data(data_full_autocorr_merged_bin_biol,type="no transformation")
y=totaluniquevals(a)
specieslist.SC<-specieslist

stringToQuoser <- function(varName) {
  wrapr::let(c(VARNAME = varName), quo(VARNAME))
}

for (j in 1:length(specieslist.SC)){
  response <- stringToQuoser(specieslist.SC[j])
  data_full_autocorr_merged_bin_biol_detected<-data_full_autocorr_merged_bin_biol %>%
    dplyr::group_by(Code_Transect_Person) %>%
    dplyr::summarize(presence=sum((!!response)))
  data_full_autocorr_merged_bin_biol_for_model=data_full_autocorr_merged_bin_biol[which(data_full_autocorr_merged_bin_biol$Code_Transect_Person %in% data_full_autocorr_merged_bin_biol_detected$Code_Transect_Person[which(data_full_autocorr_merged_bin_biol_detected$presence!=0)]),]
  if (length(which(data_full_autocorr_merged_bin_biol_detected$presence!=0))>1){
    if (length(unique(data_full_autocorr_merged_bin_biol_for_model$Code_Transect))>1 & length(unique(data_full_autocorr_merged_bin_biol_for_model$Person))>1){mbin=glmer(as.formula(paste(specieslist.SC[j],"~1+Repeat+(1|Code_Transect)+(1|Person)")), data = data_full_autocorr_merged_bin_biol_for_model, family = binomial)
    }
    if (length(unique(data_full_autocorr_merged_bin_biol_for_model$Code_Transect))==1){mbin=glmer(as.formula(paste(specieslist.SC[j],"~1+Repeat+(1|Person)")), data = data_full_autocorr_merged_bin_biol_for_model, family = binomial)
    }
    if (length(unique(data_full_autocorr_merged_bin_biol_for_model$Person))==1){mbin=glmer(as.formula(paste(specieslist.SC[j],"~1+Repeat+(1|Code_Transect)")), data = data_full_autocorr_merged_bin_biol_for_model, family = binomial)
    }
  }
  else {mbin=glm(as.formula(paste(specieslist.SC[j],"~1+Repeat")), data = data_full_autocorr_merged_bin_biol_for_model, family = binomial)}
  print(summary(mbin))
  r=as.data.frame(summary(mbin)$coefficients)
  rownames(r)[1]=specieslist.SC[j]
  if (j==1){
    p=r
  } else {p=rbind(p,r)}
  data_full_autocorr_merged_bin_biol_for_graph<-data_full_autocorr_merged_bin_biol_for_model[,c(specieslist.SC[j],"Repeat","Code_Transect","Person")]
  data_full_autocorr_merged_bin_biol_for_graph$Code_Transect_Person<-paste(data_full_autocorr_merged_bin_biol_for_graph$Code_Transect,data_full_autocorr_merged_bin_biol_for_graph$Person)
  data_full_autocorr_merged_bin_biol_for_graph[,specieslist.SC[j]]=as.factor(data_full_autocorr_merged_bin_biol_for_graph[,specieslist.SC[j]])
  data_full_autocorr_merged_bin_biol_for_graph[,"Code_Transect_Person"]=as.factor(data_full_autocorr_merged_bin_biol_for_graph[,"Code_Transect_Person"])
  g1<-ggplot(data=data_full_autocorr_merged_bin_biol_for_graph,aes_string(x="Repeat",y=specieslist.SC[j]))+clean_theme()+geom_point(position = position_jitter(w = 0, h = 0.2),aes_string(color="Code_Transect_Person",shape=specieslist.SC[j]))+theme(legend.position = "none")+clean_theme+ggtitle(specieslist.SC[j])
    #Plot presence and absence in function of ordered repeat with different colors for different transects
 print(g1)
}
p[,c("Estimate","Std. Error","z value")]=round(p[,c("Estimate","Std. Error","z value")],digits = 2)
p[,c("Pr(>|z|)")]=round(p[,c("Pr(>|z|)")],digits = 6)
```

```{r}
#ACF (Autocorrelation function) for 18 repeats
data_full_autocorr_merged_cont=merge(data_full_autocorr,autocorrelation_check_data,by=c("Location","Transect","Person","Repeat"))
data_full_autocorr_merged_cont=data_full_autocorr_merged_cont[order(data_full_autocorr_merged_cont$Location,data_full_autocorr_merged_cont$Transect,data_full_autocorr_merged_cont$Order),]
data=data_full_autocorr_merged_cont
data.repeat.50.SC=data.repeat.50[which(data.repeat.50$Island=="SantaCruz"),]
x=Transformation_data(data.repeat.50.SC,type="no transformation")
specieslist.SC<-specieslist[-which(specieslist %in% names(which(colSums(x)==0)))]
specieslist.SC=specieslist
df=as.data.frame(matrix(ncol=9,nrow=length(specieslist.SC)))
rownames(df)=specieslist.SC
for (i in 1:length(specieslist.SC)){
  x=as.data.frame(data[,c(specieslist.SC[i])])
  x<-sqrt(sqrt(x))
  p=as.data.frame(matrix(t(x), ncol=540/18, 
          byrow=FALSE), stringsAsFactors=FALSE)
  p=p[, colSums(p != 0) > 0]
  if (is.data.frame(p)==FALSE){
    rownumber=1
  } else {rownumber=ncol(p)}
  empty.df <- as.data.frame(matrix(ncol=9,nrow=rownumber))
  for (j in 1:rownumber){
    if (is.data.frame(p)==FALSE){z=p
    } else {z=p[,j]}
    acf_object=acf(z, na.action = na.pass,
    main = "Auto-correlation plot for residuals")
    print(acf_object)
    empty.df[j,]=acf_object$acf
  }
  df[i,]=col_means(empty.df)
}
data_full_autocorr_merged_cont_df_acf=df
data_full_autocorr_merged_cont_df_acf=round(data_full_autocorr_merged_cont_df_acf,digits=2)
```

```{r}
#PACF (Partial Autocorrelation function) for 18 repeats
data_full_autocorr_merged_cont=merge(data_full_autocorr,autocorrelation_check_data,by=c("Location","Transect","Person","Repeat"))
data_full_autocorr_merged_cont=data_full_autocorr_merged_cont[order(data_full_autocorr_merged_cont$Location,data_full_autocorr_merged_cont$Transect,data_full_autocorr_merged_cont$Order),]
data=data_full_autocorr_merged_cont
df=as.data.frame(matrix(ncol=12,nrow=length(specieslist)))
rownames(df)=specieslist
for (i in 1:length(specieslist)){
  x=as.data.frame(data[,c(specieslist[i])])
  x<-sqrt(sqrt(x))
  p=as.data.frame(matrix(t(x), ncol=540/18, 
          byrow=FALSE), stringsAsFactors=FALSE)
  p=p[, colSums(p != 0) > 0]
  if (is.data.frame(p)==FALSE){
    rownumber=1
  } else {rownumber=ncol(p)}
  empty.df <- as.data.frame(matrix(ncol=12,nrow=rownumber))
  for (j in 1:rownumber){
    if (is.data.frame(p)==FALSE){z=p
    } else {z=p[,j]}
    acf_object=pacf(z, na.action = na.pass,
    main = "Auto-correlation plot for residuals")
    print(acf_object)
    empty.df[j,]=acf_object$acf
  }
  df[i,]=col_means(empty.df)
}
data_full_autocorr_merged_cont_df_pacf=df
```

```{r}
#Generate boxplots per factor
general_boxplot<-function(data.repeat.50,response){
  print(ggboxplot(data=data.repeat.50, x = "Island", y = response,main=response))
  print(ggboxplot(data=data.repeat.50, x = "Location", y = response, color = "Island",main=response))
  print(ggboxplot(data=data.repeat.50, x = "Code_Transect", y = response, color = "Location",main=response))
  print(ggboxplot(data=data.repeat.50, x = "Code", y = response, color = "Location",main=response))
  print(ggboxplot(data=data.repeat.50, x = "Code", y = response, color = "Person",main=response))

}

```

```{r}
general_boxplot(data.repeat.50,"amarillosnapper")
```

```{r}
for (i in unique(data.repeat.50$Location)){
  for (j in unique(data.repeat.50$Transect)){
    for (k in unique(data.repeat.50$Person)){
      print(plot(as.numeric(data.repeat.50$Repeat[which(data.repeat.50$Location==i & 
                                  data.repeat.50$Transect==j &
                                  data.repeat.50$Person==k)]),
           data.repeat.50$totalamountofspecies[which(data.repeat.50$Location==i & 
                                  data.repeat.50$Transect==j &
                                  data.repeat.50$Person==k)]))
    }
  }
}
plot(data.repeat.50$Repeat,data.repeat.50$totalamountofspecies)
```

```{r echo=FALSE}
#Basic NMDS
BASIC_NMDS<-function(data.repeat){
  set.seed(123)
  community_matrix=Transformation_data(data.repeat,"no transformation")
  if (any(rowSums(community_matrix)==0)){
    data.repeat=data.repeat[-which(rowSums(community_matrix)==0),]
    community_matrix=community_matrix[-which(rowSums(community_matrix)==0),]
  }
  
  data_NMDS=metaMDS(community_matrix, # Our community-by-species matrix
                       k=2, # The number of reduced dimensions
                    trymax=1) 
  
  stressplot(data_NMDS)
  print(plot(data_NMDS))
  ordiplot(data_NMDS,type="n")
  ordihull(data_NMDS,groups=data.repeat$Location,draw="polygon",col="grey90",label=F)
  orditorp(data_NMDS,display="species",col="red",air=0.01)
  orditorp(data_NMDS,display="sites",col=c(rep("green",5),rep("blue",5)),
     air=0.01,cex=0.1)
}
```

```{r echo=FALSE}
BASIC_NMDS(data.repeat.50)
```

```{r}
#Plot results of permanova as pie
Personal_pyplot<-function(data,title,type){
  if (type=="adonis"){
    data=data$aov.tab
  }
  data=data[-nrow(data),]
  s <- list(
    family = "Times New Roman",
    size = 35,
    color = 'white')
  
  m <- list(
    l = 100,
    r = 100,
    b = 200,
    t = 100,
    pad = 4
  )
  substrRight <- function(x, n){
  substr(x, nchar(x)-n+1, nchar(x))
  }
  abiotic.biotic <- plot_ly(sort=FALSE) %>% 
    add_pie(data=data, labels = rownames(data), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = FALSE,
            domain = list(x = c(0, 0.47), y = c(0, 1))) %>%
    layout(title = title,
            xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
            yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),font=t,
           margin=m) 
    #add_annotations(a)
  print(abiotic.biotic)
  g<-ggplot(data=data,aes(x=rownames(data),y=R2))
  g<-g+geom_bar(stat="identity")
  g<-g+theme(axis.text.x = element_text(angle = 90, hjust = 1))+xlab("Factor")+ylab("R?")+ylim(low=0, high=1)
  print(g)
}
```

```{r}
#Plot results of permanova as multiple pies
Personal_pyplot_multiple<-function(data.10,data.20,data.30,data.40,data.50,type){
  if (type=="adonis"){
    data=data$aov.tab
  }
  data=data[-nrow(data),]
  s <- list(
    family = "Times New Roman",
    size = 35,
    color = 'white')
  
  m <- list(
    l = 100,
    r = 100,
    b = 200,
    t = 100,
    pad = 4
  )
  abiotic.biotic <- plot_ly(sort=FALSE) %>% 
    add_pie(data=data.10, labels = rownames(data.10), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = TRUE,
            domain = list(x = c(0, 0.31), y = c(0, 0.45))) %>%
    add_pie(data=data.20, labels = rownames(data.20), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = FALSE,
            domain = list(x = c(0.34, 0.65), y = c(0, 0.45))) %>%
    add_pie(data=data.30, labels = rownames(data.30), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = FALSE,
            domain = list(x = c(0.68, 1.0), y = c(0, 0.45))) %>%
    add_pie(data=data.40, labels = rownames(data.40), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = FALSE,
            domain = list(x = c(0, 0.31), y = c(0.55, 1))) %>%
    add_pie(data=data.50, labels = rownames(data.50), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = FALSE,
            domain = list(x = c(0.34, 0.65), y = c(0.55, 1))) %>%
    layout(#title = 'Use of abiotic and biotic data acquisition methods in SDM studies of fish which incorporate movement',
            xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
            yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),font=t,
           margin=m) 
    #add_annotations(a)
  print(abiotic.biotic)
}
```

```{r}
#Plot results of permanova as 2 pies
Personal_pyplot_pair<-function(data.10,data.20,type){
  if (type=="adonis"){
    data.10=data.10$aov.tab
    data.20=data.20$aov.tab
  }
  data.10=data.10[-nrow(data.10),]
  data.20=data.20[-nrow(data.20),]
  s <- list(
    family = "Times New Roman",
    size = 35,
    color = 'white')
  
  m <- list(
    l = 100,
    r = 100,
    b = 200,
    t = 100,
    pad = 4
  )
  abiotic.biotic <- plot_ly(sort=FALSE) %>% 
    add_pie(data=data.10, labels = rownames(data.10), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = TRUE,
            domain = list(x = c(0, 0.45), y = c(0, 47))) %>%
    add_pie(data=data.20, labels = rownames(data.20), values = ~R2, type = 'pie',
            textposition = 'outside',
            textinfo = 'label+percent',
            #insidetextfont = list(color = '#FFFFFF'),
            insidetextfont = s,
            #hoverinfo = 'text',
            #text = ~paste( Amount, ' publications'),
            marker = list(colors = colors,
                          line = list(color = '#FFFFFF', width = 1)),
            #The 'pull' attribute can also be used to create space between the sectors
            showlegend = FALSE,
            domain = list(x = c(0.55, 1.00), y = c(0, 47))) %>%
    # add_pie(data=data.30, labels = rownames(data.30), values = ~R2, type = 'pie',
    #         textposition = 'outside',
    #         textinfo = 'label+percent',
    #         #insidetextfont = list(color = '#FFFFFF'),
    #         insidetextfont = s,
    #         #hoverinfo = 'text',
    #         #text = ~paste( Amount, ' publications'),
    #         marker = list(colors = colors,
    #                       line = list(color = '#FFFFFF', width = 1)),
    #         #The 'pull' attribute can also be used to create space between the sectors
    #         showlegend = FALSE,
    #         domain = list(x = c(0.68, 1.0), y = c(0, 0.45))) %>%
    # add_pie(data=data.40, labels = rownames(data.40), values = ~R2, type = 'pie',
    #         textposition = 'outside',
    #         textinfo = 'label+percent',
    #         #insidetextfont = list(color = '#FFFFFF'),
    #         insidetextfont = s,
    #         #hoverinfo = 'text',
    #         #text = ~paste( Amount, ' publications'),
    #         marker = list(colors = colors,
    #                       line = list(color = '#FFFFFF', width = 1)),
    #         #The 'pull' attribute can also be used to create space between the sectors
    #         showlegend = FALSE,
    #         domain = list(x = c(0, 0.31), y = c(0.55, 1))) %>%
    # add_pie(data=data.50, labels = rownames(data.50), values = ~R2, type = 'pie',
    #         textposition = 'outside',
    #         textinfo = 'label+percent',
    #         #insidetextfont = list(color = '#FFFFFF'),
    #         insidetextfont = s,
    #         #hoverinfo = 'text',
    #         #text = ~paste( Amount, ' publications'),
    #         marker = list(colors = colors,
    #                       line = list(color = '#FFFFFF', width = 1)),
    #         #The 'pull' attribute can also be used to create space between the sectors
    #         showlegend = FALSE,
    #         domain = list(x = c(0.34, 0.65), y = c(0.55, 1))) %>%
    layout(#title = 'Use of abiotic and biotic data acquisition methods in SDM studies of fish which incorporate movement',
            xaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),
            yaxis = list(showgrid = FALSE, zeroline = FALSE, showticklabels = FALSE),font=t,
           margin=m) 
    #add_annotations(a)
  print(abiotic.biotic)
  return(abiotic.biotic)
}
```

PERMANOVA results testing for differences in number of species indicate no significant effect of island and person analyzing the videos. The order of the variables does not have an effect because of the balanced design. 

```{r}
#Turn empty elements (NA) into 0 values
data.repeat.10[is.na(data.repeat.10)==TRUE]=0
data.repeat.20[is.na(data.repeat.20)==TRUE]=0
data.repeat.30[is.na(data.repeat.30)==TRUE]=0
data.repeat.40[is.na(data.repeat.40)==TRUE]=0
data.repeat.50[is.na(data.repeat.50)==TRUE]=0
```


```{r}
#PERMANOVA species density
totalamountofspecies<-data.repeat.10$totalamountofspecies
perm.species.amount.10<-adonis2(totalamountofspecies~Island + Location %in% Island + Code_Transect %in% Location + Person + Person:Island + Person:Location + Person:Code_Transect,data=data.repeat.10, permutations = 9)
print(perm.species.amount.10)
totalamountofspecies<-data.repeat.20$totalamountofspecies
perm.species.amount.20<-adonis2(totalamountofspecies~Island + Location %in% Island + Code_Transect %in% Location + Person + Person:Island + Person:Location + Person:Code_Transect,data=data.repeat.20, permutations = 9)
print(perm.species.amount.20)
totalamountofspecies<-data.repeat.30$totalamountofspecies
perm.species.amount.30<-adonis2(totalamountofspecies~Island + Location %in% Island + Code_Transect %in% Location + Person + Person:Island + Person:Location + Person:Code_Transect,data=data.repeat.30, permutations = 9)
print(perm.species.amount.30)
totalamountofspecies<-data.repeat.40$totalamountofspecies
perm.species.amount.40<-adonis2(totalamountofspecies~Island + Location %in% Island + Code_Transect %in% Location + Person + Person:Island + Person:Location + Person:Code_Transect,data=data.repeat.40, permutations = 9)
print(perm.species.amount.40)
totalamountofspecies<-data.repeat.50$totalamountofspecies
perm.species.amount.50<-adonis2(totalamountofspecies~Island + Location %in% Island + Code_Transect %in% Location + Person + Person:Island + Person:Location + Person:Code_Transect,data=data.repeat.50, permutations = 9)
print(perm.species.amount.50)

```

```{r}
#plot results permanova species density
Personal_pyplot(perm.species.amount.10,"PERMANOVA of species richness (10 meter transects)","adonis2")
Personal_pyplot(perm.species.amount.20,"PERMANOVA of species richness (20 meter transects)","adonis2")
Personal_pyplot(perm.species.amount.30,"PERMANOVA of species richness (30 meter transects)","adonis2")
Personal_pyplot(perm.species.amount.40,"PERMANOVA of species richness (40 meter transects)","adonis2")
Personal_pyplot(perm.species.amount.50,"PERMANOVA of species richness (50 meter transects)","adonis2")
```

```{r echo=FALSE}
#Determine Bray Curtis Dissimilarities and perform PERMANOVA for entire dataset
Personal_PERMANOVA<-function(data.repeat,factors,response,algo,type,transform="4root",method='bray',binary=FALSE){
  #set.seed(123)
  fish.mat=Transformation_data(data.repeat,transform)
  if (any(rowSums(fish.mat)==0)){
    data.repeat=data.repeat[-which(rowSums(fish.mat)==0),]
    fish.mat=fish.mat[-which(rowSums(fish.mat)==0),]
  }
  fish.dist=vegdist(fish.mat, method=method,binary=binary)
  .form=as.formula(paste(response,"~", paste(factors, collapse=algo)))
  if (type=="adonis2"){
    fish.div<-adonis2(.form, data=data.repeat, permutations = 999, method=method)
  }
  if (type=="adonis"){
    fish.div<-adonis(.form, data=data.repeat, permutations = 999, method=method)
  }
  print(fish.div)
  print(densityplot(permustats(fish.div)))
  return(fish.div)
}
#Determine Bray Curtis Dissimilarities and perform PERMANOVA for entire dataset using strata
Personal_PERMANOVA_strata<-function(data.repeat,.form,type){
  fish.mat=Transformation_data(data.repeat,"4root")
  if (any(rowSums(fish.mat)==0)){
    data.repeat=data.repeat[-which(rowSums(fish.mat)==0),]
    fish.mat=fish.mat[-which(rowSums(fish.mat)==0),]
  }
  fish.dist=vegdist(fish.mat, method='bray')
  if (type=="adonis2"){
    fish.div<-adonis2(.form, data=data.repeat, permutations = 999, method="bray")
  }
  if (type=="adonis"){
    fish.div<-adonis(.form, data=data.repeat, permutations = 999, method="bray")
  }
  print(fish.div)
  print(densityplot(permustats(fish.div)))
  return(fish.div)
}
```

```{r}
#Run different PERMANOVA analyses for structure fish communities using different methods to calculate the dissimilarity matrix and differnt formulae notations

fish.div.data.repeat.10<-Personal_PERMANOVA(data.repeat.10,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis")
fish.div.data.repeat.20<-Personal_PERMANOVA(data.repeat.20,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis")
fish.div.data.repeat.30<-Personal_PERMANOVA(data.repeat.30,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis")
fish.div.data.repeat.40<-Personal_PERMANOVA(data.repeat.40,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis")
fish.div.data.repeat.50<-Personal_PERMANOVA(data.repeat.50,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis")

fish.div.data.repeat.10.jac<-Personal_PERMANOVA(data.repeat.10,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",method="jaccard")
fish.div.data.repeat.20.jac<-Personal_PERMANOVA(data.repeat.20,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",method="jaccard")
fish.div.data.repeat.30.jac<-Personal_PERMANOVA(data.repeat.30,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",method="jaccard")
fish.div.data.repeat.40.jac<-Personal_PERMANOVA(data.repeat.40,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",method="jaccard")
fish.div.data.repeat.50.jac<-Personal_PERMANOVA(data.repeat.50,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",method="jaccard")

fish.div.data.repeat.10.sor<-Personal_PERMANOVA(data.repeat.10,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",binary=TRUE)
fish.div.data.repeat.20.sor<-Personal_PERMANOVA(data.repeat.20,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",binary=TRUE)
fish.div.data.repeat.30.sor<-Personal_PERMANOVA(data.repeat.30,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",binary=TRUE)
fish.div.data.repeat.40.sor<-Personal_PERMANOVA(data.repeat.40,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",binary=TRUE)
fish.div.data.repeat.50.sor<-Personal_PERMANOVA(data.repeat.50,c('Island','Location','Code_Transect','Person'),'fish.dist','*',"adonis",binary=TRUE)

fish.div.data.repeat.50.strata.1<-Personal_PERMANOVA(data.repeat.50,c('Island','Location','Code_Transect','Person'),'fish.dist','+',"adonis")
fish.div.data.repeat.50.strata.2<-Personal_PERMANOVA(data.repeat.50,c('Person','Location','Code_Transect','Island'),'fish.dist','+',"adonis")
fish.div.data.repeat.50.strata.3<-Personal_PERMANOVA_strata(data.repeat.50,as.formula(paste('fish.dist ~ Island + Location + Code_Transect + Person')),"adonis")
fish.div.data.repeat.50.strata.4<-Personal_PERMANOVA_strata(data.repeat.50,as.formula(paste('fish.dist ~ Island + Location %in% Island + Code_Transect %in% Location')),"adonis")
fish.div.data.repeat.50.strata.5<-Personal_PERMANOVA_strata(data.repeat.50,as.formula(paste('fish.dist ~ Island + Location %in% Island + Code_Transect %in% Location + Person + Person:Island + Person:Location + Person:Code_Transect')),"adonis")
fish.div.data.repeat.50.strata.6<-Personal_PERMANOVA_strata(data.repeat.50,as.formula(paste('fish.dist ~ Island/Location/Code_Transect + Person + Person:Island + Person:Location + Person:Code_Transect')),"adonis")
fish.div.data.repeat.50.strata.7<-Personal_PERMANOVA_strata(data.repeat.50,as.formula(paste('fish.dist ~ Island + Code_Transect %in% Location + Location %in% Island + Person')),"adonis")

#Different formulae notations yield the same result.
```

```{r}
#Plot results permanova structure fish communities
rownames(fish.div.data.repeat.10$aov.tab)[3]="Transect"
rownames(fish.div.data.repeat.10$aov.tab)[4]="Observer"
rownames(fish.div.data.repeat.10$aov.tab)[5]="Island:Observer"
rownames(fish.div.data.repeat.10$aov.tab)[6]="Location:Observer"
rownames(fish.div.data.repeat.10$aov.tab)[7]="Transect:Observer"
rownames(fish.div.data.repeat.50$aov.tab)[3]="Transect"
rownames(fish.div.data.repeat.50$aov.tab)[4]="Observer"
rownames(fish.div.data.repeat.50$aov.tab)[5]="Island:Observer"
rownames(fish.div.data.repeat.50$aov.tab)[6]="Location:Observer"
rownames(fish.div.data.repeat.50$aov.tab)[7]="Transect:Observer"
Personal_pyplot(fish.div.data.repeat.10,"PERMANOVA of fish community (10 meter transects)","adonis")
Personal_pyplot(fish.div.data.repeat.20,"PERMANOVA of fish community (20 meter transects)","adonis")
Personal_pyplot(fish.div.data.repeat.30,"PERMANOVA of fish community (30 meter transects)","adonis")
Personal_pyplot(fish.div.data.repeat.40,"PERMANOVA of fish community (40 meter transects)","adonis")
Personal_pyplot(fish.div.data.repeat.50,"PERMANOVA of fish community (50 meter transects)","adonis")
Personal_pyplot_pair(fish.div.data.repeat.10,fish.div.data.repeat.50,"adonis")
```

```{r echo=FALSE}
#Assess multivariate dispersion
Personal_DISPERSION<-function(data.repeat,group){
  set.seed(123)
  fish.mat=Transformation_data(data.repeat,"4root")
  if (any(rowSums(fish.mat)==0)){
    data.repeat=data.repeat[-which(rowSums(fish.mat)==0),]
    fish.mat=fish.mat[-which(rowSums(fish.mat)==0),]
  }
  fish.dist=vegdist(fish.mat, method='bray')
  dispersion<-betadisper(fish.dist, group=lapply(data.repeat[,group],as.character)[[1]])
  dispersion
  print(anova(dispersion))
  boxplot(dispersion,xlab=group) #plot average distance to the centroid
  print(permutest(dispersion))
  plot(dispersion, hull=TRUE, ellipse=TRUE,label=TRUE,main=group,xlab="PCoA1",ylab="PCoA2") #sd ellipse: Higher spread: Higher betadiversity  
}
Personal_DISPERSION(data.repeat.10,"Location")
Personal_DISPERSION(data.repeat.20,"Location")
Personal_DISPERSION(data.repeat.30,"Location")
Personal_DISPERSION(data.repeat.40,"Location")
Personal_DISPERSION(data.repeat.50,"Location")
Personal_DISPERSION(data.repeat[which(data.repeat$Person=="Amber"),],"Location")
Personal_DISPERSION(data.repeat[which(data.repeat$Person=="Long"),],"Location")
Personal_DISPERSION(data.repeat[which(data.repeat$Person=="Heleen"),],"Location")
Personal_DISPERSION(data.repeat,"Location")
Personal_DISPERSION(data.repeat.10,"Person")
Personal_DISPERSION(data.repeat.20,"Person")
Personal_DISPERSION(data.repeat.30,"Person")
Personal_DISPERSION(data.repeat.40,"Person")
Personal_DISPERSION(data.repeat.50,"Person")
Personal_DISPERSION(data.repeat.10,"Code_Transect")
Personal_DISPERSION(data.repeat.20,"Code_Transect")
Personal_DISPERSION(data.repeat.30,"Code_Transect")
Personal_DISPERSION(data.repeat.40,"Code_Transect")
Personal_DISPERSION(data.repeat.50,"Code_Transect")
Personal_DISPERSION(data.repeat.10,"Island")
Personal_DISPERSION(data.repeat.20,"Island")
Personal_DISPERSION(data.repeat.30,"Island")
Personal_DISPERSION(data.repeat.40,"Island")
```

##Plotting of NMDS of all 10 locations with group: Transect

##Plotting of NMDS at three different sample durations

##Assessment of precision of species richness and H with data pooled over 1.Persons and 2.Transects and 3.Persons and Transects. For this we will use bootstraps.

```{r}
#Create vector with random numbers
personal_RANDOM_VECTOR<-function(number.of.repeats){
  floor(runif(number.of.repeats, min=1, max=19))
}
```

```{r}
#3 to 18 repeats
# Sets string to type allowing input in functions
stringToQuoser <- function(varName) {
  wrapr::let(c(VARNAME = varName), quo(VARNAME))
}
# determine univariate precision as the inverse of the standard error over the mean
determine_precision<-function(data.repeat,response,TransectLength){
  data.repeat[which(is.na(data.repeat[,response])==TRUE),response]=0
  response <- stringToQuoser(response)
  combinations <- expand.grid(Location=unique(data.repeat$Location),Transect=unique(data.repeat$Transect),Repeat=c(3:18),stringsAsFactors = FALSE)
  combinations$precision_average<-NA
  combinations$precision_sd<-NA
  data.repeat.split=split(data.repeat,f=list(data.repeat$Location,data.repeat$Transect))
  for (i in 1:length(data.repeat.split)){
    Location=data.repeat.split[[i]][[1,"Location"]]
    Transect=data.repeat.split[[i]][[1,"Transect"]]
    for (number.of.repeats in 3:18){
      precision=vector(mode="double",length=10)
      for (j in 1:10){
        x=data.repeat.split[[i]][personal_RANDOM_VECTOR(number.of.repeats),]
        x_estimations<-x %>%
        dplyr::summarize(average_SR=mean((!!response),na.rm=TRUE),
                          sd_SR=sd((!!response),na.rm=TRUE))
        precision[j]=(x_estimations$sd_SR/sqrt(number.of.repeats))/x_estimations$average_SR
      }
      precision_average=mean(precision,na.rm=TRUE)
      precision_sd=sd(precision,na.rm=TRUE)
      combinations$precision_average[which(combinations$Location==Location & combinations$Transect==Transect & combinations$Repeat==number.of.repeats)]=precision_average
      combinations$precision_sd[which(combinations$Location==Location & combinations$Transect==Transect & combinations$Repeat==number.of.repeats)]=precision_sd
    }
  }
  combinations$total_distance<-TransectLength*combinations$Repeat
  return(combinations)
}
#Determine the average precision per repeat with confidence interval
average_precision_per_repeat<-function(combinations){
  k=nrow(combinations)/length(unique(combinations$Repeat))
  precision<-combinations %>%
    dplyr::group_by(Repeat) %>%
    dplyr::summarize(precision=mean(precision_average,na.rm=TRUE),
                     precision_sd=sqrt(sum(precision_sd^2,na.rm=TRUE)/k))
  precision$low_conf_mean<-precision$precision-qt(0.975,df=k-1)*precision$precision_sd/sqrt(k)
  precision$high_conf_mean<-precision$precision+qt(0.975,df=k-1)*precision$precision_sd/sqrt(k)
  return(precision)
}
#Combine precision estimates
combine_combinations<-function(combo1,combo2,combo3,combo4,combo5){
  combo.combo<-rbind(combo1,combo2,combo3,combo4,combo5)
  k=nrow(combo.combo)/(length(unique(combo.combo$Repeat))*length(unique(combo.combo$TransectLength)))
  combo.combo.average<-combo.combo %>%
    dplyr::group_by(Repeat,TransectLength) %>%
    dplyr::summarize(precision_average=mean(precision_average,na.rm=TRUE),
                     precision_sd=sqrt(sum(precision_sd^2,na.rm=TRUE)/k))
  combo.combo.average$total.distance<-combo.combo.average$Repeat*combo.combo.average$TransectLength
  combo.combo.average$average_ratio=(1/combo.combo.average$precision_average)/combo.combo.average$total.distance
  g<-ggplot(data=combo.combo.average,aes(x=Repeat,y=average_ratio))+geom_point(aes(color=factor(TransectLength)))
  print(g)
  return(combo.combo.average)
}

```

```{r}
#precision for species density
combinations.10.SR<-determine_precision(data.repeat.10,"totalamountofspecies",10)
combinations.20.SR<-determine_precision(data.repeat.20,"totalamountofspecies",20)
combinations.30.SR<-determine_precision(data.repeat.30,"totalamountofspecies",30)
combinations.40.SR<-determine_precision(data.repeat.40,"totalamountofspecies",40)
combinations.50.SR<-determine_precision(data.repeat.50,"totalamountofspecies",50)
```

```{r}
#precision for H
combinations.10.H<-determine_precision(data.repeat.10,"H",10)
combinations.20.H<-determine_precision(data.repeat.20,"H",20)
combinations.30.H<-determine_precision(data.repeat.30,"H",30)
combinations.40.H<-determine_precision(data.repeat.40,"H",40)
combinations.50.H<-determine_precision(data.repeat.50,"H",50)
```

```{r}
#precision for count amarillosnapper
combinations.10.amarillosnapper<-determine_precision(data.repeat.10,"amarillosnapper",10)
combinations.20.amarillosnapper<-determine_precision(data.repeat.20,"amarillosnapper",20)
combinations.30.amarillosnapper<-determine_precision(data.repeat.30,"amarillosnapper",30)
combinations.40.amarillosnapper<-determine_precision(data.repeat.40,"amarillosnapper",40)
combinations.50.amarillosnapper<-determine_precision(data.repeat.50,"amarillosnapper",50)
```

```{r}
#combinations for precision for all species
for (i in 1:length(specieslist)){
  directory=paste("./combinations/",specieslist[i],sep="")
  dir.create(directory)
  combinations.loop.10<-determine_precision(data.repeat.10,specieslist[i],10)
  filename=paste(directory,"/combinations.loop.10.csv",sep="")
  write.csv(combinations.loop.10,filename)

  combinations.loop.20<-determine_precision(data.repeat.20,specieslist[i],20)
  filename=paste(directory,"/combinations.loop.20.csv",sep="")
  write.csv(combinations.loop.20,filename)

  combinations.loop.30<-determine_precision(data.repeat.30,specieslist[i],30)
  filename=paste(directory,"/combinations.loop.30.csv",sep="")
  write.csv(combinations.loop.30,filename)

  combinations.loop.40<-determine_precision(data.repeat.40,specieslist[i],40)
  filename=paste(directory,"/combinations.loop.40.csv",sep="")
  write.csv(combinations.loop.40,filename)

  combinations.loop.50<-determine_precision(data.repeat.50,specieslist[i],50)
  filename=paste(directory,"/combinations.loop.50.csv",sep="")
  write.csv(combinations.loop.50,filename)
}
```

```{r warning=FALSE}
#Determine precision for different distances
precision.10<-average_precision_per_repeat(combinations.10.SR)
precision.20<-average_precision_per_repeat(combinations.20.SR)
precision.30<-average_precision_per_repeat(combinations.30.SR)
precision.40<-average_precision_per_repeat(combinations.40.SR)
precision.50<-average_precision_per_repeat(combinations.50.SR)
precision.10$distance<-10
precision.20$distance<-20
precision.30$distance<-30
precision.40$distance<-40
precision.50$distance<-50
precision.10$TransectLength<-"10 meter"
precision.20$TransectLength<-"20 meter"
precision.30$TransectLength<-"30 meter"
precision.40$TransectLength<-"40 meter"
precision.50$TransectLength<-"50 meter"
precision.combo<-rbind(precision.10,precision.20,precision.30,precision.40,precision.50)

precision.combo$total.distance<-precision.combo$Repeat*precision.combo$distance
precision.combo$ratio1=(1/precision.combo$precision)/precision.combo$total.distance
precision.combo$ratio2=(precision.combo$precision)/precision.combo$total.distance

g1<-ggplot(data = precision.combo,aes(x=Repeat,y=precision,group=TransectLength))
g1<-g1+geom_line(aes(colour=TransectLength),size=1)+geom_point()
xmax=20
ymax=0.25
g1<-g1+xlab("Number of repeats")+ylab("SE/mean")+xlim(0,xmax)+ylim(0,ymax)
g1<-g1+geom_ribbon(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.2)+
  theme(legend.title=element_text(size=10), legend.text=element_text(size=10),
                           legend.justification=c(0.25,0.25),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=8,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.25, linetype = 1, lineend = "butt"))+
          annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(A)" ,size=4,family="serif")
# g<-g+geom_errorbar(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,colour=TransectLength),alpha=1)
A<-g1
A

a<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio1))+geom_point(aes(color=TransectLength))
a
b<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio2))+geom_point(aes(color=TransectLength))
b
xmax=1000
ymax=0.25
c<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=TransectLength))+geom_line(aes(color=TransectLength))+xlim(0,xmax)+ylim(0,ymax)+xlab("Total distance (m)")+ylab("SE/mean")
c<-c+theme(legend.title=element_text(size=10), legend.text=element_text(size=10),
                           legend.justification=c(0.25,0.25),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=8,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.25, linetype = 1, lineend = "butt"))+
          annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(B)" ,size=4,family="serif")
c<-c+geom_errorbar(data=precision.combo,aes(x=total.distance,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.6)
B<-c
B
precision.combo$fRepeat<-as.factor(precision.combo$Repeat)
d<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=fRepeat))
d
```

```{r warning=FALSE}
#Determine precision for different distances: H
precision.10<-average_precision_per_repeat(combinations.10.H)
precision.20<-average_precision_per_repeat(combinations.20.H)
precision.30<-average_precision_per_repeat(combinations.30.H)
precision.40<-average_precision_per_repeat(combinations.40.H)
precision.50<-average_precision_per_repeat(combinations.50.H)
precision.10$distance<-10
precision.20$distance<-20
precision.30$distance<-30
precision.40$distance<-40
precision.50$distance<-50
precision.10$TransectLength<-"10 meter"
precision.20$TransectLength<-"20 meter"
precision.30$TransectLength<-"30 meter"
precision.40$TransectLength<-"40 meter"
precision.50$TransectLength<-"50 meter"
precision.combo<-rbind(precision.10,precision.20,precision.30,precision.40,precision.50)

precision.combo$total.distance<-precision.combo$Repeat*precision.combo$distance
precision.combo$ratio1=(1/precision.combo$precision)/precision.combo$total.distance
precision.combo$ratio2=(precision.combo$precision)/precision.combo$total.distance

g2<-ggplot(data = precision.combo,aes(x=Repeat,y=precision,group=TransectLength))
g2<-g2+geom_line(aes(colour=TransectLength),size=1)+geom_point()
xmax=20
ymax=0.4
g2<-g2+xlab("Number of repeats")+ylab("SE/mean")+xlim(0,xmax)+ylim(0,ymax)
g2<-g2+geom_ribbon(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.2)+
  theme(legend.title=element_text(size=10), legend.text=element_text(size=10),
                           legend.justification=c(0.25,0.25),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=8,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.25, linetype = 1, lineend = "butt"))+
          annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(C)" ,size=4,family="serif")
# g<-g+geom_errorbar(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,colour=TransectLength),alpha=1)
C<-g2
C
#jpeg("./figures/overleaf/precision_SR_and_H.jpeg",width = 600,height=1000)
#grid.arrange(g1,g2)
#dev.off()

a<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio1))+geom_point(aes(color=TransectLength))
a
b<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio2))+geom_point(aes(color=TransectLength))
b
c<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=TransectLength))+geom_line(aes(color=TransectLength))
xmax=1000
ymax=0.4
c<-c+xlim(0,xmax)+ylim(0,ymax)+xlab("Total distance (m)")+ylab("SE/mean")
c<-c+
  theme(legend.title=element_text(size=10), legend.text=element_text(size=10),
                           legend.justification=c(0.25,0.25),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=8,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.25, linetype = 1, lineend = "butt"))+
          annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(D)" ,size=4,family="serif")
c<-c+geom_errorbar(data=precision.combo,aes(x=total.distance,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.6)
D<-c
D
precision.combo$fRepeat<-as.factor(precision.combo$Repeat)
d<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=fRepeat))
d
```

```{r warning=FALSE}
#Determine precision for different distances: amarillosnapper
precision.10<-average_precision_per_repeat(combinations.10.amarillosnapper)
precision.20<-average_precision_per_repeat(combinations.20.amarillosnapper)
precision.30<-average_precision_per_repeat(combinations.30.amarillosnapper)
precision.40<-average_precision_per_repeat(combinations.40.amarillosnapper)
precision.50<-average_precision_per_repeat(combinations.50.amarillosnapper)
precision.10$distance<-10
precision.20$distance<-20
precision.30$distance<-30
precision.40$distance<-40
precision.50$distance<-50
precision.10$TransectLength<-"10 meter"
precision.20$TransectLength<-"20 meter"
precision.30$TransectLength<-"30 meter"
precision.40$TransectLength<-"40 meter"
precision.50$TransectLength<-"50 meter"
precision.combo<-rbind(precision.10,precision.20,precision.30,precision.40,precision.50)

precision.combo$total.distance<-precision.combo$Repeat*precision.combo$distance
precision.combo$ratio1=(1/precision.combo$precision)/precision.combo$total.distance
precision.combo$ratio2=(precision.combo$precision)/precision.combo$total.distance

g2<-ggplot(data = precision.combo,aes(x=Repeat,y=precision,group=TransectLength))
g2<-g2+geom_line(aes(colour=TransectLength),size=1)+geom_point()
xmax=20
ymax=0.8
g2<-g2+xlab("Number of repeats")+ylab("SE/mean")+xlim(0,xmax)+ylim(0,ymax)
g2<-g2+geom_ribbon(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.2)+
  theme(legend.title=element_text(size=20), legend.text=element_text(size=10),
                           legend.justification=c(0.5,0.5),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))+
          annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(A)" ,size=8,family="serif")
# g<-g+geom_errorbar(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,colour=TransectLength),alpha=1)
PAN1<-g2
PAN1
#jpeg("./figures/overleaf/precision_SR_and_H.jpeg",width = 600,height=1000)
#grid.arrange(g1,g2)
#dev.off()

a<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio1))+geom_point(aes(color=TransectLength))
a
b<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio2))+geom_point(aes(color=TransectLength))
b
c<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=TransectLength))+geom_line(aes(color=TransectLength))
xmax=1000
ymax=0.8
c<-c+xlim(0,xmax)+ylim(0,ymax)+xlab("Total distance (m)")+ylab("SE/mean")
c<-c+theme(legend.title=element_text(size=20), legend.text=element_text(size=10),
                           legend.justification=c(0.5,0.5),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))+
          annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(B)" ,size=8,family="serif")
c<-c+geom_errorbar(data=precision.combo,aes(x=total.distance,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.6)
PAN2<-c
PAN2
precision.combo$fRepeat<-as.factor(precision.combo$Repeat)
d<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=fRepeat))
d

```

```{r warning=FALSE}
#Determine precision for different distances: all species
for (i in 1:length(specieslist)){
  directory=paste("./combinations/",specieslist[i],sep="")
  filename10=paste(directory,"/combinations.loop.10.csv",sep="")
  combinations.10=read.csv(filename10,stringsAsFactors = FALSE)
  precision.10<-average_precision_per_repeat(combinations.10)
  filename20=paste(directory,"/combinations.loop.20.csv",sep="")
  combinations.20=read.csv(filename20,stringsAsFactors = FALSE)
  precision.20<-average_precision_per_repeat(combinations.20)
  filename30=paste(directory,"/combinations.loop.30.csv",sep="")
  combinations.30=read.csv(filename30,stringsAsFactors = FALSE)
  precision.30<-average_precision_per_repeat(combinations.30)
  filename40=paste(directory,"/combinations.loop.40.csv",sep="")
  combinations.40=read.csv(filename40,stringsAsFactors = FALSE)
  precision.40<-average_precision_per_repeat(combinations.40)
  filename50=paste(directory,"/combinations.loop.50.csv",sep="")
  combinations.50=read.csv(filename50,stringsAsFactors = FALSE)
  precision.50<-average_precision_per_repeat(combinations.50)
  precision.10$distance<-10
  precision.20$distance<-20
  precision.30$distance<-30
  precision.40$distance<-40
  precision.50$distance<-50
  precision.10$TransectLength<-"10 meter"
  precision.20$TransectLength<-"20 meter"
  precision.30$TransectLength<-"30 meter"
  precision.40$TransectLength<-"40 meter"
  precision.50$TransectLength<-"50 meter"
  precision.combo<-rbind(precision.10,precision.20,precision.30,precision.40,precision.50)
  
  precision.combo$total.distance<-precision.combo$Repeat*precision.combo$distance
  precision.combo$ratio1=(1/precision.combo$precision)/precision.combo$total.distance
  precision.combo$ratio2=(precision.combo$precision)/precision.combo$total.distance
  
  g2<-ggplot(data = precision.combo,aes(x=Repeat,y=precision,group=TransectLength))
  g2<-g2+geom_line(aes(colour=TransectLength),size=1)+geom_point()
  xmax=20
  ymax=1.2
  g2<-g2+xlab("Number of repeats")+ylab("SE/mean")+xlim(0,xmax)+ylim(0,ymax)+ggtitle(specieslist[i])
  g2<-g2+geom_ribbon(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.2)+theme(legend.title=element_text(size=20), legend.text=element_text(size=20),
                             legend.justification=c(0.5,0.5),legend.key.size =  unit(0.2, "in"),
                             legend.position=c(0.80, 0.7),
                             #panel.grid.major = element_blank(),
                             axis.line = element_line(colour = "black"),
                             text=element_text(size=16,  family="serif"),
                             panel.background = element_rect(fill = "white", colour = NA),
                             panel.grid.major = element_line(colour = "gray"),
                             panel.grid.minor = element_blank(),
                             axis.title = element_text(size = rel(1), colour = "black"),
                             axis.text = element_text(size = rel(1), colour = "black"),
                             line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))+
            annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(G)" ,size=8,family="serif")
  # g<-g+geom_errorbar(data=precision.combo,aes(x=Repeat,ymin=low_conf_mean,ymax=high_conf_mean,colour=TransectLength),alpha=1)
  PANFANG1<-g2
  print(PANFANG1)
  #jpeg("./figures/overleaf/precision_SR_and_H.jpeg",width = 600,height=1000)
  #grid.arrange(g1,g2)
  #dev.off()
  
  a<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio1))+geom_point(aes(color=TransectLength))
  a
  b<-ggplot(data=precision.combo,aes(x=Repeat,y=ratio2))+geom_point(aes(color=TransectLength))
  b
  c<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=TransectLength))+geom_line(aes(color=TransectLength))
  xmax=1000
  ymax=1.2
  c<-c+xlim(0,xmax)+ylim(0,ymax)+xlab("Total distance (m)")+ylab("SE/mean")+ggtitle(specieslist[i])
  c<-c+theme(legend.title=element_text(size=20), legend.text=element_text(size=20),
                             legend.justification=c(0.5,0.5),legend.key.size =  unit(0.2, "in"),
                             legend.position=c(0.80, 0.7),
                             #panel.grid.major = element_blank(),
                             axis.line = element_line(colour = "black"),
                             text=element_text(size=16,  family="serif"),
                             panel.background = element_rect(fill = "white", colour = NA),
                             panel.grid.major = element_line(colour = "gray"),
                             panel.grid.minor = element_blank(),
                             axis.title = element_text(size = rel(1), colour = "black"),
                             axis.text = element_text(size = rel(1), colour = "black"),
                             line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))+
            annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(H)" ,size=8,family="serif")
  c<-c+geom_errorbar(data=precision.combo,aes(x=total.distance,ymin=low_conf_mean,ymax=high_conf_mean,fill=TransectLength,colour=TransectLength),alpha=0.6)
  PANFANG2<-c
  print(PANFANG2)
  precision.combo$fRepeat<-as.factor(precision.combo$Repeat)
  d<-ggplot(data=precision.combo,aes(x=total.distance,y=precision))+geom_point(aes(color=fRepeat))
  d
}
```

```{r}
data=combinations.50.SR
data$Loc_Transect=paste(data$Location,data$Transect)
data$low_conf_mean<-data$precision_average-qt(0.975,df=data$Repeat-1)*data$precision_sd/sqrt(data$Repeat)
data$high_conf_mean<-data$precision_average+qt(0.975,df=data$Repeat-1)*data$precision_sd/sqrt(data$Repeat)
g<-ggplot(data = data,aes(x=Repeat,y=precision_average,group=Loc_Transect))
g<-g+geom_point(aes(colour=Loc_Transect),size=2)
g<-g+xlab("Number of repeats")+ylab("SE/mean")+xlim(0,18)+ylim(0,0.30)
g
```

```{r}
#Pooled sub-samples into replicates
#Adapted from Anderson, 2015 (Measures of precision for dissimilarity-based multivariate analysis of ecological communities)
#Histogram function 

myhist = function(d,breaks) {
  n.nan = sum(is.nan(d))
  my.breaks = (0:breaks)/breaks
  v=hist(d, breaks = my.breaks,xlim=c(-0.1,1),las=1,
        main = "", xlab = "", ylab = "")
  print(v)
  points(-0.075,n.nan,pch = 19,cex = 1)
  text(-0.075,0.0,"NaN",pos = 3)
  return(v$counts)
}
mydens = function(d) {
  plot(density(d,from=-0.1,to=1))
}
mypool = function(Y,ipool) {
  #Y: dissimilarity matrix
  #ipool: number of observations to take together
  N = dim(Y)[1]
  ngroup = floor(N/ipool)
  group = factor(rep(1:ngroup, each = ipool) )
  subset = Y[1:length(group),]
  pooled = rowsum(subset, group)
  D.pooled = round(vegdist(pooled, measure = "bray"),9)
  return(D.pooled)
}
mypool.max = function(Y,ipool) {
  #Takes together subsequantial samples (structure of the data is important)
  N = dim(Y)[1]
  ngroup = floor(N/ipool)
  group = factor(rep(1:ngroup, each = ipool) )
  subset = Y[1:length(group),]
  subset$group<-group
  pooled<-subset %>%
    dplyr::group_by(group) %>%
    dplyr::summarize_all(max)
  pooled$group<-NULL
  D.pooled = round(vegdist(pooled, measure = "bray"),9)
  return(D.pooled)
}
mypool.max.random = function(Y,ipool) {
  #Takes together random samples (structure of the data is not important)
  N = dim(Y)[1]
  ngroup = floor(N/ipool)
  group = factor(rep(1:ngroup, each = ipool) )
  group = group[shuffle(group)]
  subset = Y[1:length(group),]
  subset$group<-group
  pooled<-subset %>%
    dplyr::group_by(group) %>%
    dplyr::summarize_all(max)
  pooled$group<-NULL
  D.pooled = round(vegdist(pooled, measure = "bray"),9)
  return(D.pooled)
}
Pooled.samples<-function(data.repeat,group,breaks,order){
  runloop=unique(data.repeat[,group])
  SCA <- expand.grid(splitted=lapply(runloop,as.character)[[1]],number_pooled=c(1:6),stringsAsFactors = FALSE)
  empty.df <- as.data.frame(matrix(ncol=breaks,nrow=nrow(SCA))) #Create empty dataframe to store dissimilarity values
  empty.df$splitted=SCA$splitted 
  empty.df$number_pooled=SCA$number_pooled
  for (i in 1:nrow(runloop)){ #Run through all the different locations!!!!!!!!!!!!!!!!!!! We only look at the dissimilary values within one location! So we have 10 samples!
    BC=data.repeat[which(data.repeat[,group]==as.character(runloop[i,1])),] #Take the data of location i
    BC.fish<-Transformation_data(BC,"4 root") #Take the fish data and transform it
    D.BC = vegdist(BC.fish, measure = "bray") #Determine the dissimilarity values (each subsample = replicate)
    
    for (ipool in 1:6){
      
      par(mfrow = c(1,1), mar = c(3, 3, 1, 1))
      
      # n = 1 (original)
      if (ipool==1){ # each subsample = replicate
        D.1 = D.BC
        x=t(myhist(D.1,breaks))
        text(-0.075, 0.8*2000, "n = 1", pos = 4, cex = 1.3)
      }
      else{
        if (order=="strict"){
          D = mypool.max(BC.fish,ipool) #each ipool number of subsamples = replicate
          x=t(myhist(D,breaks))
          text(-0.075, 0.8*500, "n = 2", pos = 4, cex = 1.3)
        }
        if (order=="random"){
          D = mypool.max.random(BC.fish,ipool) #each ipool number of subsamples = replicate
          x=t(myhist(D,breaks))
          text(-0.075, 0.8*500, "n = 2", pos = 4, cex = 1.3)
        }
      }
      empty.df[which(empty.df$number_pooled==ipool & empty.df$splitted==as.character(runloop[i,1])),1:ncol(x)]=x #store dissimilarity values
    }
  }
  return(empty.df)
}
#Order of repeats is important when pooling repeats
Pooled.analysis.strict.order<-function(){
  Pooled.analysis<-Pooled.samples(data.repeat.10,"Code_Transect",10,"strict")
  Pooled.analysis_original<-Pooled.analysis
  Pooled.analysis_original=Pooled.analysis_original[order(Pooled.analysis_original$splitted),]
  
  Pooled.analysis$splitted<-NULL
  
  Pooled.analysis.repeats<-Pooled.analysis %>%
    dplyr::group_by(number_pooled) %>%
    dplyr::summarize_all(mean)
  summ<-apply(Pooled.analysis.repeats[-c(1)],1,sum)
  for (i in 1:nrow(Pooled.analysis.repeats)){
    Pooled.analysis.repeats[i,c(2:ncol(Pooled.analysis.repeats))]=Pooled.analysis.repeats[i,c(2:ncol(Pooled.analysis.repeats))]/summ[i]
  }
  Pooled.analysis.repeats<-as.data.frame(Pooled.analysis.repeats)
  Pooled.analysis.repeats=melt(data=Pooled.analysis.repeats,id="number_pooled")
  #Pooled.analysis.repeats=Pooled.analysis.repeats[which(Pooled.analysis.repeats$number_pooled==1 | Pooled.analysis.repeats$number_pooled==2 | Pooled.analysis.repeats$number_pooled==3),]
  g<-ggplot(data=Pooled.analysis.repeats,aes(x=variable,y=value,group=number_pooled))
  g<-g+geom_line(aes(colour=number_pooled),size=2)+scale_colour_gradient(low="coral", high="steelblue")
  g
  for (i in 1:6){
    h<-ggplot(data=Pooled.analysis.repeats[which(Pooled.analysis.repeats$number_pooled==i),],aes(x=variable,y=value))
    h<-h+geom_bar(stat="identity")+coord_cartesian(ylim = c(0, 0.4))
    print(h)
  }
}
#Order of repeats is not important when pooling repeats
Pooled.analysis.random.order<-function(data,group,order){
  Pooled.analysis<-list()
  Pooled.analysis.repeats<-list()
  Pooled.analysis.repeats.sd<-list()
  for (repeats in 1:10){ #number of times the Pooled.samples function is run (at the end the average is taken)
    Pooled.analysis[[repeats]]<-Pooled.samples(data,group,breaks=10,order)
    Pooled.analysis[[repeats]]$splitted<-NULL
    
    Pooled.analysis.repeats[[repeats]]<-Pooled.analysis[[repeats]] %>% #there are 60 observations (10 locations and 6 ways to take subsamples together (number_pooled))
      dplyr::group_by(number_pooled) %>% #pooling over location return one value per number_pooled
      dplyr::summarize_all(mean)
    Pooled.analysis.repeats.sd[[repeats]]<-Pooled.analysis[[repeats]] %>%
      dplyr::group_by(number_pooled) %>%
      dplyr::summarize_all(sd)
    summ<-apply(Pooled.analysis.repeats[[repeats]][-c(1)],1,sum) #total amount of dissimilarity values for a specific number_pooled
    summ.sd<-apply(Pooled.analysis.repeats.sd[[repeats]][-c(1)],1,sum)
    for (i in 1:nrow(Pooled.analysis.repeats[[repeats]])){
      Pooled.analysis.repeats[[repeats]][i,c(2:ncol(Pooled.analysis.repeats[[repeats]]))]=Pooled.analysis.repeats[[repeats]][i,c(2:ncol(Pooled.analysis.repeats[[repeats]]))]/summ[i] #Turn amount into percentage
    }
    for (i in 1:nrow(Pooled.analysis.repeats.sd[[repeats]])){
      Pooled.analysis.repeats.sd[[repeats]][i,c(2:ncol(Pooled.analysis.repeats.sd[[repeats]]))]=Pooled.analysis.repeats.sd[[repeats]][i,c(2:ncol(Pooled.analysis.repeats.sd[[repeats]]))]/(summ[i])
    }
    Pooled.analysis.repeats[[repeats]]=as.matrix(Pooled.analysis.repeats[[repeats]]) #from list to matrix
    Pooled.analysis.repeats.sd[[repeats]]=as.matrix(Pooled.analysis.repeats.sd[[repeats]])
  }
  Pooled.analysis.repeats=mean.list(Pooled.analysis.repeats) #mean over the number of times the Pooled.samples function is run (repeats in for loop)
  k=length(Pooled.analysis.repeats.sd)
  for (i in 1:k){
    Pooled.analysis.repeats.sd[[i]][,2:ncol(Pooled.analysis.repeats.sd[[i]])]<-Pooled.analysis.repeats.sd[[i]][,2:ncol(Pooled.analysis.repeats.sd[[i]])]^2
  }
  Pooled.analysis.repeats.sd=sqrt(Reduce("+",Pooled.analysis.repeats.sd)/k)
  Pooled.analysis.repeats.sd<-as.data.frame(Pooled.analysis.repeats.sd)
  Pooled.analysis.repeats.sd$number_pooled=1:nrow(Pooled.analysis.repeats.sd)
  Pooled.analysis.repeats<-as.data.frame(Pooled.analysis.repeats)
  Pooled.analysis.repeats=melt(data=Pooled.analysis.repeats,id="number_pooled")
  Pooled.analysis.repeats.sd=melt(data=Pooled.analysis.repeats.sd,id="number_pooled")
  Pooled.analysis.repeats$sd<-Pooled.analysis.repeats.sd$value
  Pooled.analysis.repeats$low_conf_mean<-NA
  Pooled.analysis.repeats$high_conf_mean<-NA
  vector=(0:length(unique(Pooled.analysis.repeats$variable)))/length(unique(Pooled.analysis.repeats$variable))
  v=list()
  for (i in 1:length(unique(Pooled.analysis.repeats$variable))){
    v[[i]]=paste(as.character(vector[i]),as.character(vector[i+1]),sep="-")
  }
  v=setNames(v,unique(Pooled.analysis.repeats$variable))
  Pooled.analysis.repeats$variable=as.character(Pooled.analysis.repeats$variable)
  for (i in 1:length(names(v))){
    Pooled.analysis.repeats$variable[which(Pooled.analysis.repeats$variable==(names(v)[i]))]=(v[[i]])
  }
  g<-ggplot(data=Pooled.analysis.repeats,aes(x=variable,y=value,group=number_pooled))
  g<-g+geom_line(aes(colour=number_pooled),size=2)+scale_colour_gradient(low="coral", high="steelblue")
  print(g)
  for (i in 1:6){
    h<-ggplot(data=Pooled.analysis.repeats[which(Pooled.analysis.repeats$number_pooled==i),],aes(x=variable,y=value))
    h<-h+geom_bar(stat="identity")+coord_cartesian(ylim = c(0, 0.4))
    print(h)
  }
  Pooled.analysis.repeats$number_pooled=as.factor(Pooled.analysis.repeats$number_pooled)
  h<-ggplot(data=Pooled.analysis.repeats,aes(x=variable,y=value,fill=number_pooled))
  h<-h+geom_bar(stat="identity",position=position_dodge())+coord_cartesian(ylim = c(0, 0.4))+scale_fill_manual("legend", values = c("1" = "black", "2" = "#003300", "3" = "#006600", "4" = "#33CC33","5" = "#66FF33","6" = "#CCFF66"))
  print(h)
  Pooled.analysis.repeats$number_pooled=as.numeric(Pooled.analysis.repeats$number_pooled)
  return(Pooled.analysis.repeats)
}
#Create plots for pooled repeats
plot.Pooled.analysis<-function(Pooled.analysis.repeats,tit){
  g<-ggplot(data=Pooled.analysis.repeats,aes(x=variable,y=value,group=number_pooled))
  g<-g+geom_line(aes(colour=number_pooled),size=2)+scale_colour_gradient(low="coral", high="steelblue")
  print(g)
  Pooled.analysis.repeats$number_pooled=as.factor(Pooled.analysis.repeats$number_pooled)
  h<-ggplot(data=Pooled.analysis.repeats,aes(x=variable,y=value,fill=number_pooled))
  h<-h+geom_bar(stat="identity",position=position_dodge())+coord_cartesian(ylim = c(0, 0.4))+scale_fill_manual("observations\n pooled", values = c("1" = "black", "2" = "#003300", "3" = "#006600", "4" = "#33CC33","5" = "#66FF33","6" = "#CCFF66"))+ylab("percentage")+xlab("dissimilarity values")+
    theme(
                           #legend.position="centre",
                           legend.title=element_text(size=10), legend.text=element_text(size=10),
                           legend.justification=c(0.5,0.5),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = 9, colour = "black"),
                           axis.text = element_text(size = 7, colour = "black"),
                           axis.text.x = element_text(angle = 45,hjust = 1),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt"))+
    annotate("text", x=7, y=0.35, label= tit ,size=3,family="serif")
  print(h)
  return(h)
}

#Grouping based on location, order of repeats is not important
Pooled.analysis.random.order.10.Location<-Pooled.analysis.random.order(data.repeat.10,"Location","random")
Pooled.analysis.random.order.20.Location<-Pooled.analysis.random.order(data.repeat.20,"Location","random")
Pooled.analysis.random.order.30.Location<-Pooled.analysis.random.order(data.repeat.30,"Location","random")
Pooled.analysis.random.order.40.Location<-Pooled.analysis.random.order(data.repeat.40,"Location","random")
Pooled.analysis.random.order.50.Location<-Pooled.analysis.random.order(data.repeat.50,"Location","random")

a1<-plot.Pooled.analysis(Pooled.analysis.random.order.10.Location,"Transect length: 10 m \n Pooled within Location")
a2<-plot.Pooled.analysis(Pooled.analysis.random.order.20.Location,"Transect length: 20 m \n Pooled within Location")
a3<-plot.Pooled.analysis(Pooled.analysis.random.order.30.Location,"Transect length: 30 m \n Pooled within Location")
a4<-plot.Pooled.analysis(Pooled.analysis.random.order.40.Location,"Transect length: 40 m \n Pooled within Location")
a5<-plot.Pooled.analysis(Pooled.analysis.random.order.50.Location,"Transect length: 50 m \n Pooled within Location")
grid.arrange(a1,a2,a3,a4,a5)

#Grouping based on transect, order of repeats is not important
Pooled.analysis.random.order.10.Transect<-Pooled.analysis.random.order(data.repeat.10,"Code_Transect","random")
Pooled.analysis.random.order.20.Transect<-Pooled.analysis.random.order(data.repeat.20,"Code_Transect","random")
Pooled.analysis.random.order.30.Transect<-Pooled.analysis.random.order(data.repeat.30,"Code_Transect","random")
Pooled.analysis.random.order.40.Transect<-Pooled.analysis.random.order(data.repeat.40,"Code_Transect","random")
Pooled.analysis.random.order.50.Transect<-Pooled.analysis.random.order(data.repeat.50,"Code_Transect","random")

b1<-plot.Pooled.analysis(Pooled.analysis.random.order.10.Transect,"Transect length: 10 m \n Pooled within Transect")
b2<-plot.Pooled.analysis(Pooled.analysis.random.order.20.Transect,"Transect length: 20 m \n Pooled within Transect")
b3<-plot.Pooled.analysis(Pooled.analysis.random.order.30.Transect,"Transect length: 30 m \n Pooled within Transect")
b4<-plot.Pooled.analysis(Pooled.analysis.random.order.40.Transect,"Transect length: 40 m \n Pooled within Transect")
b5<-plot.Pooled.analysis(Pooled.analysis.random.order.50.Transect,"Transect length: 50 m \n Pooled within Transect")
grid.arrange(b1,b2,b3,b4,b5)

#Grouping based on location, order of repeats is important
Pooled.analysis.strict.order.10<-Pooled.analysis.random.order(data.repeat.10,"Location","strict")
Pooled.analysis.strict.order.20<-Pooled.analysis.random.order(data.repeat.20,"Location","strict")
Pooled.analysis.strict.order.30<-Pooled.analysis.random.order(data.repeat.30,"Location","strict")
Pooled.analysis.strict.order.40<-Pooled.analysis.random.order(data.repeat.40,"Location","strict")
Pooled.analysis.strict.order.50<-Pooled.analysis.random.order(data.repeat.50,"Location","strict")

plot.Pooled.analysis(Pooled.analysis.strict.order.10,"")
plot.Pooled.analysis(Pooled.analysis.strict.order.20,"")
plot.Pooled.analysis(Pooled.analysis.strict.order.30,"")
plot.Pooled.analysis(Pooled.analysis.strict.order.40,"")
plot.Pooled.analysis(Pooled.analysis.strict.order.50,"")
```

```{r}
#Adapted from Anderson, 2015 (Measures of precision for dissimilarity-based multivariate analysis of ecological communities)
#Histogram function 
#Determine precentage of uninformative dissimilarity values 
myhist.nan = function(d) {
  n.nan = sum(is.nan(d))
  n.0 = length(which(d==0))
  n.1 = length(which(d==1))
  n.nan.0.1=c(n.nan,n.0,n.1)
  return(n.nan.0.1)
}

mypool.max.random = function(Y,ipool) {
  #Takes together random samples (structure of the data is not important)
  N = dim(Y)[1]
  ngroup = floor(N/ipool)
  group = factor(rep(1:ngroup, each = ipool) )
  group = group[shuffle(group)]
  subset = Y[1:length(group),]
  subset$group<-group
  pooled<-subset %>%
    dplyr::group_by(group) %>%
    dplyr::summarize_all(max)
  pooled$group<-NULL
  D.pooled = round(vegdist(pooled, measure = "bray"),9)
  return(D.pooled)
}

Pooled.samples.nan<-function(data.repeat,group,order){
  runloop=unique(data.repeat[,group])
  SCA <- expand.grid(splitted=lapply(runloop,as.character)[[1]],number_pooled=c(1:6),stringsAsFactors = FALSE)
  empty.df <- as.data.frame(matrix(ncol=3,nrow=nrow(SCA))) #Create empty dataframe to store dissimilarity values
  empty.df$splitted=SCA$splitted 
  empty.df$number_pooled=SCA$number_pooled
  for (i in 1:nrow(runloop)){ #Run through all the different locations!!!!!!!!!!!!!!!!!!! We only look at the dissimilary values within one location! So we have 10 samples!
    BC=data.repeat[which(data.repeat[,group]==as.character(runloop[i,1])),] #Take the data of location i
    BC.fish<-Transformation_data(BC,"4 root") #Take the fish data and transform it
    D.BC = vegdist(BC.fish, measure = "bray") #Determine the dissimilarity values (each subsample = replicate)
    
    for (ipool in 1:6){
      
      par(mfrow = c(1,1), mar = c(3, 3, 1, 1))
      
      # n = 1 (original)
      if (ipool==1){ # each subsample = replicate
        D.1 = D.BC
        x=t(myhist.nan(D.1))
      }
      else{
        if (order=="strict"){
          D = mypool.max(BC.fish,ipool) #each ipool number of subsamples = replicate
          x=t(myhist.nan(D))
        }
        if (order=="random"){
          D = mypool.max.random(BC.fish,ipool) #each ipool number of subsamples = replicate
          x=t(myhist.nan(D))
        }
      }
      empty.df[which(empty.df$number_pooled==ipool & empty.df$splitted==as.character(runloop[i,1])),1:ncol(x)]=x #store dissimilarity values
    }
  }
  return(empty.df)
}


Pooled.analysis.random.order.nan<-function(data,group,order){
  Pooled.analysis<-list()
  Pooled.analysis.repeats<-list()
  Pooled.analysis.repeats.sd<-list()
  for (repeats in 1:100){ #number of times the Pooled.samples function is run (at the end the average is taken)
    Pooled.analysis[[repeats]]<-Pooled.samples.nan(data,group,order)
    Pooled.analysis[[repeats]]$splitted<-NULL
    colnames(Pooled.analysis[[repeats]])=c("NA","0","1","number_pooled")
    Pooled.analysis.repeats[[repeats]]<-Pooled.analysis[[repeats]] %>% #there are 60 observations (10 locations and 6 ways to take subsamples together (number_pooled))
      dplyr::group_by(number_pooled) %>% #pooling over location return one value per number_pooled
      dplyr::summarize_all(mean)
    Pooled.analysis.repeats.sd[[repeats]]<-Pooled.analysis[[repeats]] %>%
      dplyr::group_by(number_pooled) %>%
      dplyr::summarize_all(sd)
    summ<-c(1431,351,153,78,45,36) #total amount of dissimilarity values for a specific number_pooled
    for (i in 1:nrow(Pooled.analysis.repeats[[repeats]])){
      Pooled.analysis.repeats[[repeats]][i,c(2:ncol(Pooled.analysis.repeats[[repeats]]))]=Pooled.analysis.repeats[[repeats]][i,c(2:ncol(Pooled.analysis.repeats[[repeats]]))]/summ[i] #Turn amount into percentage
    }
    for (i in 1:nrow(Pooled.analysis.repeats.sd[[repeats]])){
      Pooled.analysis.repeats.sd[[repeats]][i,c(2:ncol(Pooled.analysis.repeats.sd[[repeats]]))]=Pooled.analysis.repeats.sd[[repeats]][i,c(2:ncol(Pooled.analysis.repeats.sd[[repeats]]))]/(summ[i])
    }
    Pooled.analysis.repeats[[repeats]]=as.matrix(Pooled.analysis.repeats[[repeats]]) #from list to matrix
    Pooled.analysis.repeats.sd[[repeats]]=as.matrix(Pooled.analysis.repeats.sd[[repeats]])
  }
  Pooled.analysis.repeats=mean.list(Pooled.analysis.repeats) #mean over the number of times the Pooled.samples function is run (repeats in for loop)
  k=length(Pooled.analysis.repeats.sd)
  for (i in 1:k){
    Pooled.analysis.repeats.sd[[i]][,2:ncol(Pooled.analysis.repeats.sd[[i]])]<-Pooled.analysis.repeats.sd[[i]][,2:ncol(Pooled.analysis.repeats.sd[[i]])]^2
  }
  Pooled.analysis.repeats.sd=sqrt(Reduce("+",Pooled.analysis.repeats.sd)/k)
  Pooled.analysis.repeats.sd<-as.data.frame(Pooled.analysis.repeats.sd)
  Pooled.analysis.repeats.sd$number_pooled=1:nrow(Pooled.analysis.repeats.sd)
  Pooled.analysis.repeats<-as.data.frame(Pooled.analysis.repeats)
  Pooled.analysis.repeats=melt(data=Pooled.analysis.repeats,id="number_pooled")
  Pooled.analysis.repeats.sd=melt(data=Pooled.analysis.repeats.sd,id="number_pooled")
  Pooled.analysis.repeats$sd<-Pooled.analysis.repeats.sd$value
  Pooled.analysis.repeats$low_conf_mean<-qt(0.0975,df=k-1)*Pooled.analysis.repeats$sd/k
  Pooled.analysis.repeats$high_conf_mean<-qt(0.0975,df=k-1)*Pooled.analysis.repeats$sd/k
  
  Pooled.analysis.repeats$sd<-Pooled.analysis.repeats$sd*100
  Pooled.analysis.repeats$value<-Pooled.analysis.repeats$value*100
  Pooled.analysis.repeats$low_conf_mean<-Pooled.analysis.repeats$low_conf_mean*100
  Pooled.analysis.repeats$high_conf_mean<-Pooled.analysis.repeats$high_conf_mean*100
  
  Pooled.analysis.repeats[,c("value","sd","low_conf_mean","high_conf_mean")]=round(Pooled.analysis.repeats[,c("value","sd","low_conf_mean","high_conf_mean")],digits = 4)

  return(Pooled.analysis.repeats)
}

pooled.nan.10.location<-Pooled.analysis.random.order.nan(data=data.repeat.10,"Location","random")
pooled.nan.20.location<-Pooled.analysis.random.order.nan(data=data.repeat.20,"Location","random")
pooled.nan.30.location<-Pooled.analysis.random.order.nan(data=data.repeat.30,"Location","random")
pooled.nan.40.location<-Pooled.analysis.random.order.nan(data=data.repeat.40,"Location","random")
pooled.nan.50.location<-Pooled.analysis.random.order.nan(data=data.repeat.50,"Location","random")

pooled.nan.10.location$TransectLength<-"10"
pooled.nan.20.location$TransectLength<-"20"
pooled.nan.30.location$TransectLength<-"30"
pooled.nan.40.location$TransectLength<-"40"
pooled.nan.50.location$TransectLength<-"50"
pooled.nan.location<-rbind(pooled.nan.10.location,pooled.nan.20.location,pooled.nan.30.location,pooled.nan.40.location,pooled.nan.50.location)
pooled.nan.location <- dcast(pooled.nan.location, number_pooled + variable ~ TransectLength, value.var="value")
pooled.nan.location <- pooled.nan.location[order(pooled.nan.location$variable),]

pooled.nan.10.transect<-Pooled.analysis.random.order.nan(data=data.repeat.10,"Code_Transect","random")
pooled.nan.20.transect<-Pooled.analysis.random.order.nan(data=data.repeat.20,"Code_Transect","random")
pooled.nan.30.transect<-Pooled.analysis.random.order.nan(data=data.repeat.30,"Code_Transect","random")
pooled.nan.40.transect<-Pooled.analysis.random.order.nan(data=data.repeat.40,"Code_Transect","random")
pooled.nan.50.transect<-Pooled.analysis.random.order.nan(data=data.repeat.50,"Code_Transect","random")

pooled.nan.10.transect$TransectLength<-"10"
pooled.nan.20.transect$TransectLength<-"20"
pooled.nan.30.transect$TransectLength<-"30"
pooled.nan.40.transect$TransectLength<-"40"
pooled.nan.50.transect$TransectLength<-"50"
pooled.nan.transect<-rbind(pooled.nan.10.transect,pooled.nan.20.transect,pooled.nan.30.transect,pooled.nan.40.transect,pooled.nan.50.transect)
pooled.nan.transect <- dcast(pooled.nan.transect, number_pooled + variable ~ TransectLength, value.var="value")
pooled.nan.transect <- pooled.nan.transect[order(pooled.nan.transect$variable),]
```

```{r}
#Multivariate precision function
#Adapted from Anderson, 2015 (Measures of precision for dissimilarity-based multivariate analysis of ecological communities)
#per transect: complex structure of nested and crossed factors not taken into account. The average per transect is taken.
MSEgroup.d = function (D, group, nresamp = 10, ...) {
  
  # Some necessary preliminary functions:            
  mult.SE = function (d) {
    n = dim(as.matrix(d))[1]
    ss = sum(d^2)/n
    v = ss/(n-1)
    x = sqrt(v/n)
    return(x)
  }
  quant.upper = function(x) quantile(x, prob = 0.975, na.rm = TRUE)
  quant.lower = function(x) quantile(x, prob = 0.025, na.rm = TRUE)
  
  # Getting parameters of the problem
  group = factor(group)
  ng = length(levels(group))
  n.i = table(group) 
  
  # Ensure distance matrix is in the form of a matrix (rather than a "distance" object)
  D = as.matrix(D)
  
  # Setting up the matrices for results
  means <- means.b <- lower <- upper <- matrix(rep(0,ng*max(n.i)),ncol = max(n.i), nrow = ng)
  colnames(means) <- colnames(lower) <- colnames(upper) <- 1:max(n.i)
  rownames(means) <- rownames(lower) <- rownames(upper) <- levels(group)
  
  # Loop - do this for each group
  for (igroup in 1:ng) {
    subset.D = D[ group==levels(group)[igroup] , group==levels(group)[igroup] ]
    
    # One matrix is used to store the values under permutation resampling for each sample size
    multSE.store.p = matrix(rep(0,nresamp*n.i[igroup]), ncol = n.i[igroup], nrow = nresamp)
    # One matrix is used to store the values under bootstrap resampling for each sample size
    multSE.store.b = matrix(rep(0,nresamp*n.i[igroup]), ncol = n.i[igroup], nrow = nresamp)
    
    # Bootstrap loop for each sample size.
    for (nsub in 2:n.i[igroup]) {
      for (iresamp in 1:nresamp) {
        ivec.p = sample(1:n.i[igroup], size = nsub, replace = FALSE)
        ivec.b = sample(1:n.i[igroup], size = nsub, replace = TRUE)
        D.perm = subset.D[ivec.p,ivec.p]
        D.boot = subset.D[ivec.b,ivec.b]
        multSE.store.p[iresamp,nsub] = mult.SE(as.dist(D.perm))
        multSE.store.b[iresamp,nsub] = mult.SE(as.dist(D.boot))
      }
    }
    
    # Means and quantiles
    means[igroup,1:n.i[igroup]] = colMeans(multSE.store.p)
    means.b[igroup,1:n.i[igroup]] = colMeans(multSE.store.b)
    upper[igroup,1:n.i[igroup]] = apply(multSE.store.b,MARGIN = 2,quant.upper)
    lower[igroup,1:n.i[igroup]] = apply(multSE.store.b,MARGIN = 2,quant.lower)
    
  } # end of loop for groups
  
  bias =  means - means.b
  lower = lower + bias
  upper = upper + bias
  return(list(means = means, lower = lower, upper = upper))
  
}
```

```{r}
#Determine multSE
RUN.MSEgroup.d<-function(data.repeat,grouping){
  Group = factor(lapply(data.repeat[,grouping],as.character)[[1]])
  Y = Transformation_data(data.repeat,"4root")
  D = vegdist(Y, method = "bray")
  output = MSEgroup.d(D, Group, nresamp = 10)
  
  ng = length(levels(Group))
  n.i = table(Group)
  nmax = max(n.i) 
  nudge = 0
  
  mycol = c("black","gray54","white")
  mypch = c(21,24,25)
  plot(3:nmax, output$means[3:nmax],type="n", main = "",
       ylab = "Multivariate pseudo SE", xlab = "Sample size (n)",
       ylim = c(0,0.3), xlim = c(1,22), las=1) 
  for (i in 1:ng) {
    arrows(3:n.i[i]+nudge, output$upper[i,3:n.i[i]],
           3:n.i[i]+nudge, output$lower[i,3:n.i[i]],
           length = 0.01, angle = 90, code = 3, col = "black")
    points(3:n.i[i]+nudge, output$means[i,3:n.i[i]], pch = mypch[i], bg = mycol[i])
    nudge = nudge + 0.20
  }
  legend(x = "topright", legend = c(levels(Group)), pch = mypch, pt.bg = mycol)
  return(output)
}
```

```{r}
#Plot multSE
Personal_output=function(data,group,distance){
  output<-RUN.MSEgroup.d(data,group)
  output[[1]]=colMeans(output[[1]],na.rm = TRUE)
  output[[2]]=colMeans(output[[2]],na.rm = TRUE)
  output[[3]]=colMeans(output[[3]],na.rm = TRUE)
  output<-as.data.frame(do.call(cbind,output))
  output$distance=distance
  output$repeats=1:nrow(output)
  return(output)
}
output=Personal_output(data.repeat.10,"Code_Transect","10 meter")
plot(3:length(output[[1]]), output$means[3:length(output[[1]])], main = "",
       ylab = "Multivariate pseudo SE", xlab = "Sample size (n)",
       ylim = c(0,0.3), xlim = c(1,length(output[[1]])), las=1) 
arrows(3:length(output[[1]]), output$upper[3:length(output[[1]])],
           3:length(output[[1]]), output$lower[3:length(output[[1]])],
           length = 0.01, angle = 90, code = 3, col = "black")
output=Personal_output(data.repeat.10,"Location","10 meter")
plot(3:length(output[[1]]), output$means[3:length(output[[1]])], main = "",
       ylab = "Multivariate pseudo SE", xlab = "Sample size (n)",
       ylim = c(0,0.3), xlim = c(1,length(output[[1]])), las=1) 
arrows(3:length(output[[1]]), output$upper[3:length(output[[1]])],
           3:length(output[[1]]), output$lower[3:length(output[[1]])],
           length = 0.01, angle = 90, code = 3, col = "black")
output.10=Personal_output(data.repeat.10,"Location","10 meter")
output.20=Personal_output(data.repeat.20,"Location","20 meter")
output.30=Personal_output(data.repeat.30,"Location","30 meter")
output.40=Personal_output(data.repeat.40,"Location","40 meter")
output.50=Personal_output(data.repeat.50,"Location","50 meter")
output=rbind(output.10,output.20,output.30,output.40,output.50)
output=output[-which(output$repeats==1),]
g<-ggplot(data = output,aes(x=repeats,y=means,group=distance))
g<-g+geom_point(aes(colour=distance))
g<-g+geom_errorbar(data=output,aes(x=repeats,ymin=lower,ymax=upper,colour=distance),alpha=0.2)
g<-g+xlab("Repeats")+ylab("Multivariate pseudo SE")
g
```

```{r}
#Multivariate precision function based on residuals PERMANOVA: takes into account that there are multiple factors
MSE.d = function (data.repeat.10, group, nresamp = 10, ...) {
  
  # Some necessary preliminary functions:            
  MSE = function(data.repeat.10) {
    type="adonis"
    perm.species.amount=Personal_PERMANOVA(data.repeat.10,c('Island','Location','Code_Transect'),'fish.dist','+',type)
    if (type=="adonis"){
      perm.species.amount=perm.species.amount$aov.tab
      MSE=perm.species.amount$SumsOfSqs[length(perm.species.amount$SumsOfSqs)-1]/perm.species.amount$Df[length(perm.species.amount$Df)-1]
    }
    if (type=="adonis2"){
      MSE=perm.species.amount$SumOfSqs[length(perm.species.amount$SumOfSqs)-1]/perm.species.amount$Df[length(perm.species.amount$Df)-1]
    }
    return(MSE)
  }
  quant.upper = function(x) quantile(x, prob = 0.975, na.rm = TRUE)
  quant.lower = function(x) quantile(x, prob = 0.025, na.rm = TRUE)
  
  # Getting parameters of the problem
  group = factor(group)
  ng = length(levels(group))
  n.i = table(group)
  nmax = min(n.i)
  N = sum(n.i)
  index = 1:N 
  
  # Setting up the vectors for the results
  # Note that these do not have to be separate whole matrices now.
  means <- means.b <- lower <- upper <- rep(0,nmax)
  
  # One matrix is used to store the values under permutation resampling for each sample size
  multSE.store.p = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  # One matrix is used to store the values under bootstrap resampling for each sample size
  multSE.store.b = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  
  # Resampling loop for each sample size.
  for (nsub in 2:nmax) {
    for (iresamp in 1:nresamp) {
      ivec.p = sample(index[group==levels(group)[1]], size = nsub, replace = FALSE)
      ivec.b = sample(index[group==levels(group)[1]], size = nsub, replace = TRUE)
      for (i in 2:ng) {
        ivec.p = c(ivec.p,sample(index[group==levels(group)[i]], size = nsub, replace = FALSE))
        ivec.b = c(ivec.b,sample(index[group==levels(group)[i]], size = nsub, replace = TRUE))
      }
      group.resamp = factor(rep(1:ng, each = nsub))
      # D.perm = D[ivec.p,ivec.p]
      # D.boot = D[ivec.b,ivec.b]
      multSE.store.p[iresamp,nsub] = sqrt(MSE(data.repeat.10[ivec.p,])/nsub) 
      multSE.store.b[iresamp,nsub] = sqrt(MSE(data.repeat.10[ivec.b,])/nsub)
    }
  }
  
  # Means and quantiles
  means = colMeans(multSE.store.p)
  means.b = colMeans(multSE.store.b)
  upper = apply(multSE.store.b,MARGIN = 2,quant.upper)
  lower = apply(multSE.store.b,MARGIN = 2,quant.lower)
  
  # Calculation of bias and completion of output
  bias =  means - means.b
  lower = lower + bias
  upper = upper + bias
  output = cbind(1:nmax, means, lower, upper)
  colnames(output) <- c("n","mean", "lower.025", "upper.975")
  return(as.data.frame(output))
  
} # end of MSE.d function

R2.d = function (data.repeat.10, group, nresamp = 10, ...) {
  
  # Some necessary preliminary functions:            
  MSE = function(data.repeat.10) {
    type="adonis"
    perm.species.amount=Personal_PERMANOVA(data.repeat.10,c('Island','Location','Code_Transect'),'fish.dist','+',type)
    if (type=="adonis"){
      perm.species.amount=perm.species.amount$aov.tab
      # R=perm.species.amount$R2
      # pseudoF=perm.species.amount$F.Model
      # MeanSqs=perm.species.amount$MeanSqs
      # Pr=perm.species.amount$`Pr(>F)`
    }
    if (type=="adonis2"){
      MSE=perm.species.amount$SumOfSqs[length(perm.species.amount$SumOfSqs)-1]/perm.species.amount$Df[length(perm.species.amount$Df)-1]
    }
    return(perm.species.amount)
  }
  quant.upper = function(x) quantile(x, prob = 0.975, na.rm = TRUE)
  quant.lower = function(x) quantile(x, prob = 0.025, na.rm = TRUE)
  
  # Getting parameters of the problem
  group = factor(group)
  ng = length(levels(group))
  n.i = table(group)
  nmax = min(n.i)
  N = sum(n.i)
  index = 1:N 
  
  # Setting up the vectors for the results
  # Note that these do not have to be separate whole matrices now.
  means <- means.b <- lower <- upper <- rep(0,nmax)
  
  # One matrix is used to store the values under permutation resampling for each sample size
  R2.store.p.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  R2.store.p.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  R2.store.p.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  pseudoF.store.p.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  pseudoF.store.p.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  pseudoF.store.p.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MeanSqs.store.p.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MeanSqs.store.p.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MeanSqs.store.p.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  Pr.store.p.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  Pr.store.p.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  Pr.store.p.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MultSA.store.p.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MultSA.store.p.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MultSA.store.p.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  # One matrix is used to store the values under bootstrap resampling for each sample size
  R2.store.b.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  R2.store.b.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  R2.store.b.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  pseudoF.store.b.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  pseudoF.store.b.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  pseudoF.store.b.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MeanSqs.store.b.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MeanSqs.store.b.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MeanSqs.store.b.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  Pr.store.b.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  Pr.store.b.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  Pr.store.b.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MultSA.store.b.island = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MultSA.store.b.location = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  MultSA.store.b.transect = matrix(rep(0,nresamp*nmax), ncol = nmax, nrow = nresamp)
  
  # Resampling loop for each sample size.
  for (nsub in 2:nmax) {
    for (iresamp in 1:nresamp) {
      ivec.p = sample(index[group==levels(group)[1]], size = nsub, replace = FALSE)
      ivec.b = sample(index[group==levels(group)[1]], size = nsub, replace = TRUE)
      for (i in 2:ng) {
        ivec.p = c(ivec.p,sample(index[group==levels(group)[i]], size = nsub, replace = FALSE))
        ivec.b = c(ivec.b,sample(index[group==levels(group)[i]], size = nsub, replace = TRUE))
      }
      group.resamp = factor(rep(1:ng, each = nsub))
      perm.species.amount.p=MSE(data.repeat.10[ivec.p,])
      perm.species.amount.b=MSE(data.repeat.10[ivec.b,])
      R2.p=perm.species.amount.p$R2
      R2.b=perm.species.amount.b$R2
      R2.store.p.island[iresamp,nsub] = R2.p[1]
      R2.store.b.island[iresamp,nsub] = R2.b[1]
      R2.store.p.location[iresamp,nsub] = R2.p[2]
      R2.store.b.location[iresamp,nsub] = R2.b[2]
      R2.store.p.transect[iresamp,nsub] = R2.p[3]
      R2.store.b.transect[iresamp,nsub] = R2.b[3]
      F.p=perm.species.amount.p$F.Model
      F.b=perm.species.amount.b$F.Model
      pseudoF.store.p.island[iresamp,nsub] = F.p[1]
      pseudoF.store.b.island[iresamp,nsub] = F.b[1]
      pseudoF.store.p.location[iresamp,nsub] = F.p[2]
      pseudoF.store.b.location[iresamp,nsub] = F.b[2]
      pseudoF.store.p.transect[iresamp,nsub] = F.p[3]
      pseudoF.store.b.transect[iresamp,nsub] = F.b[3]
      MeanSqs.p=perm.species.amount.p$MeanSqs
      MeanSqs.b=perm.species.amount.b$MeanSqs
      MeanSqs.store.p.island[iresamp,nsub] = MeanSqs.p[1]
      MeanSqs.store.b.island[iresamp,nsub] = MeanSqs.b[1]
      MeanSqs.store.p.location[iresamp,nsub] = MeanSqs.p[2]
      MeanSqs.store.b.location[iresamp,nsub] = MeanSqs.b[2]
      MeanSqs.store.p.transect[iresamp,nsub] = MeanSqs.p[3]
      MeanSqs.store.b.transect[iresamp,nsub] = MeanSqs.b[3]
      Pr.p=perm.species.amount.p$`Pr(>F)`
      Pr.b=perm.species.amount.b$`Pr(>F)`
      Pr.store.p.island[iresamp,nsub] = Pr.p[1]
      Pr.store.b.island[iresamp,nsub] = Pr.b[1]
      Pr.store.p.location[iresamp,nsub] = Pr.p[2]
      Pr.store.b.location[iresamp,nsub] = Pr.b[2]
      Pr.store.p.transect[iresamp,nsub] = Pr.p[3]
      Pr.store.b.transect[iresamp,nsub] = Pr.b[3]
      MultSA.store.p.island[iresamp,nsub] = sqrt(MeanSqs.p[1]/nsub) 
      MultSA.store.b.island[iresamp,nsub] = sqrt(MeanSqs.b[1]/nsub)
      MultSA.store.p.location[iresamp,nsub] = sqrt(MeanSqs.p[2]/nsub) 
      MultSA.store.b.location[iresamp,nsub] = sqrt(MeanSqs.b[2]/nsub)
      MultSA.store.p.transect[iresamp,nsub] = sqrt(MeanSqs.p[3]/nsub) 
      MultSA.store.b.transect[iresamp,nsub] = sqrt(MeanSqs.b[3]/nsub)
    }
  }
  
  # Means and quantiles
  
  processing.repetitions.perm<-function(R2.store.p.island,
                                        R2.store.b.island,
                                        R2.store.p.location,
                                        R2.store.b.location,
                                        R2.store.p.transect,
                                        R2.store.b.transect,name){
    R2.means.island = colMeans(R2.store.p.island)
    R2.means.b.island = colMeans(R2.store.b.island)
    R2.upper.island = apply(R2.store.b.island,MARGIN = 2,quant.upper)
    R2.lower.island = apply(R2.store.b.island,MARGIN = 2,quant.lower)
    
    R2.means.location = colMeans(R2.store.p.location)
    R2.means.b.location = colMeans(R2.store.b.location)
    R2.upper.location = apply(R2.store.b.location,MARGIN = 2,quant.upper)
    R2.lower.location = apply(R2.store.b.location,MARGIN = 2,quant.lower)
    
    R2.means.transect = colMeans(R2.store.p.transect)
    R2.means.b.transect = colMeans(R2.store.b.transect)
    R2.upper.transect = apply(R2.store.b.transect,MARGIN = 2,quant.upper)
    R2.lower.transect = apply(R2.store.b.transect,MARGIN = 2,quant.lower)
    
    # Calculation of bias and completion of output
    R2.bias.island =  R2.means.island - R2.means.b.island
    R2.lower.island = R2.lower.island + R2.bias.island
    R2.upper.island = R2.upper.island + R2.bias.island
    R2.output.island = cbind(1:nmax, R2.means.island, R2.lower.island, R2.upper.island)
    colnames(R2.output.island) <- c("n",paste(name,".mean.island",sep=""), paste(name,".lower.025.island",sep=""), paste(name,".upper.975.island",sep=""))
    
    R2.bias.location =  R2.means.location - R2.means.b.location
    R2.lower.location = R2.lower.location + R2.bias.location
    R2.upper.location = R2.upper.location + R2.bias.location
    R2.output.location = cbind(1:nmax, R2.means.location, R2.lower.location, R2.upper.location)
    colnames(R2.output.location) <- c("n",paste(name,".mean.location",sep=""), paste(name,".lower.025.location",sep=""), paste(name,".upper.975.location",sep=""))
    
    R2.bias.transect =  R2.means.transect - R2.means.b.transect
    R2.lower.transect = R2.lower.transect + R2.bias.transect
    R2.upper.transect = R2.upper.transect + R2.bias.transect
    R2.output.transect = cbind(1:nmax, R2.means.transect, R2.lower.transect, R2.upper.transect)
    colnames(R2.output.transect) <- c("n",paste(name,".mean.transect",sep=""), paste(name,".lower.025.transect",sep=""), paste(name,".upper.975.transect",sep=""))
  
    x<-list(R2.output.island,R2.output.location,R2.output.transect)
    return(x)
  }
  
  u=processing.repetitions.perm(R2.store.p.island,R2.store.b.island,R2.store.p.location,R2.store.b.location,R2.store.p.transect,R2.store.b.transect,name="R2")
  v=processing.repetitions.perm(pseudoF.store.p.island,pseudoF.store.b.island,pseudoF.store.p.location,pseudoF.store.b.location,pseudoF.store.p.transect,pseudoF.store.b.transect,name="F")
  w=processing.repetitions.perm(MeanSqs.store.p.island,MeanSqs.store.b.island,MeanSqs.store.p.location,MeanSqs.store.b.location,MeanSqs.store.p.transect,MeanSqs.store.b.transect,name="MeanSqs")
  x=processing.repetitions.perm(Pr.store.p.island,Pr.store.b.island,Pr.store.p.location,Pr.store.b.location,Pr.store.p.transect,Pr.store.b.transect,name="pvalue")
  y=processing.repetitions.perm(MultSA.store.p.island,MultSA.store.b.island,MultSA.store.p.location,MultSA.store.b.location,MultSA.store.p.transect,MultSA.store.b.transect,name="multSA")
  a=c(u,v,w,x,y)
  
  return(a)
  
} # end of MSE.d function


#######################################################################################
data.repeat.list<-list()
data.repeat.list[[1]]=data.repeat.10
data.repeat.list[[2]]=data.repeat.20
data.repeat.list[[3]]=data.repeat.30
data.repeat.list[[4]]=data.repeat.40
data.repeat.list[[5]]=data.repeat.50

output.10.permanova = MSE.d(data.repeat.10, data.repeat.10$Code_Transect, nresamp = 2)
output.10.permanova= as.data.frame(output.10.permanova)
output.20.permanova = MSE.d(data.repeat.20, data.repeat.20$Code_Transect, nresamp = 2)
output.20.permanova= as.data.frame(output.20.permanova)
output.30.permanova = MSE.d(data.repeat.30, data.repeat.30$Code_Transect, nresamp = 2)
output.30.permanova= as.data.frame(output.30.permanova)
output.40.permanova = MSE.d(data.repeat.40, data.repeat.40$Code_Transect, nresamp = 2)
output.40.permanova= as.data.frame(output.40.permanova)
output.50.permanova = MSE.d(data.repeat.50, data.repeat.50$Code_Transect, nresamp = 2)
output.50.permanova= as.data.frame(output.50.permanova)

plot.precision.permanova.single<-function(data.repeat.10,output){
  ng = length(levels(data.repeat.10$Code_Transect))
  n.i = table(data.repeat.10$Code_Transect)
  nmax = max(n.i) 
  
  plot(2:nmax, output$mean[2:nmax], type = "n", main = "",
       ylab = "MultSE based on residual mean square", xlab = "Sample size (n)",
       ylim = c(0,0.35), xlim = c(1,20), las=1) 
  arrows(2:nmax, output$upper[2:nmax],
         2:nmax, output$lower[2:nmax],
         length = 0.02, angle = 90, code = 3, col = "black")
  points(2:nmax, output$mean[2:nmax], pch = 21, bg = "black")
}
plot.precision.permanova.single(data.repeat.10,output.10.permanova)
plot.precision.permanova.single(data.repeat.20,output.20.permanova)
plot.precision.permanova.single(data.repeat.30,output.30.permanova)
plot.precision.permanova.single(data.repeat.40,output.40.permanova)
plot.precision.permanova.single(data.repeat.50,output.50.permanova)
output.10.permanova$distance<-10
output.20.permanova$distance<-20
output.30.permanova$distance<-30
output.40.permanova$distance<-40
output.50.permanova$distance<-50
output.10.permanova$TransectLength<-"10 meter"
output.20.permanova$TransectLength<-"20 meter"
output.30.permanova$TransectLength<-"30 meter"
output.40.permanova$TransectLength<-"40 meter"
output.50.permanova$TransectLength<-"50 meter"
output.permanova.combo<-rbind(output.10.permanova,
                              output.20.permanova,
                              output.30.permanova,
                              output.40.permanova,
                              output.50.permanova)
output.permanova.combo$total_distance<-output.permanova.combo$n*output.permanova.combo$distance
n.i = table(data.repeat.10$Code_Transect)
nmax = max(n.i)
output.permanova.combo.temp<-output.permanova.combo[which(output.permanova.combo$n!=1),]
xmax=20
ymax=0.3
g<-ggplot(data = output.permanova.combo.temp,aes(x=n,y=mean,group=TransectLength))
g<-g+geom_line(aes(colour=TransectLength),size=1)+geom_point()
g<-g+xlab("Number of repeats")+ylab("MultSE PERMANOVA")+xlim(0,20)+ylim(0,0.30)
g<-g+geom_ribbon(data=output.permanova.combo.temp,aes(x=n,ymin=lower.025,ymax=upper.975,fill=TransectLength,colour=TransectLength),alpha=0.2)+
    theme(
                           #legend.position="centre",
                           legend.title=element_text(size=10), legend.text=element_text(size=10),
                           legend.justification=c(0.25,0.25),legend.key.size =  unit(0.1, "in"),
                           legend.position=c(0.80, 0.7),
                           #panel.grid.major = element_blank(),
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=8,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(1), colour = "black"),
                           axis.text = element_text(size = rel(1), colour = "black"),
                           line = element_line(colour = "black", size = 0.25, linetype = 1, lineend = "butt"))+
            annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(A)" ,size=4,family="serif")

c<-ggplot(data=output.permanova.combo.temp,aes(x=total_distance,y=mean))+geom_point(aes(color=TransectLength))+geom_line(aes(color=TransectLength))
xmax=1000
ymax=0.3
c<-c+xlim(0,xmax)+ylim(0,ymax)+xlab("Total distance (m)")+ylab("MultSE PERMANOVA")
c<-c+theme(legend.title=element_text(size=10), legend.text=element_text(size=10),
                             legend.justification=c(0.25,0.25),legend.key.size =  unit(0.1, "in"),
                             legend.position=c(0.80, 0.7),
                             #panel.grid.major = element_blank(),
                             axis.line = element_line(colour = "black"),
                             text=element_text(size=8,  family="serif"),
                             panel.background = element_rect(fill = "white", colour = NA),
                             panel.grid.major = element_line(colour = "gray"),
                             panel.grid.minor = element_blank(),
                             axis.title = element_text(size = rel(1), colour = "black"),
                             axis.text = element_text(size = rel(1), colour = "black"),
                             line = element_line(colour = "black", size = 0.25, linetype = 1, lineend = "butt"))+
            annotate("text", x=xmax/10, y=ymax-ymax/10, label= "(B)" ,size=4,family="serif")
c<-c+geom_errorbar(data=output.permanova.combo.temp,aes(x=total_distance,ymin=lower.025,ymax=upper.975,fill=TransectLength,colour=TransectLength),alpha=0.6)
c
g
```

```{r}
#Plot multSE against total swim distance
output.permanova.combo.temp$total_distance<-output.permanova.combo.temp$n*output.permanova.combo.temp$distance
output.permanova.combo.temp$ratio1=(1/output.permanova.combo.temp$mean)/output.permanova.combo.temp$total_distance
output.permanova.combo.temp$ratio2=(output.permanova.combo.temp$mean)/output.permanova.combo.temp$total_distance
g<-ggplot(data=output.permanova.combo.temp,aes(x=n,y=ratio1))+geom_point(aes(color=TransectLength))
g
h<-ggplot(data=output.permanova.combo.temp,aes(x=n,y=ratio2))+geom_point(aes(color=TransectLength))
h
c<-ggplot(data=output.permanova.combo.temp,aes(x=total_distance,y=mean))+geom_point(aes(color=TransectLength))+geom_line(aes(color=TransectLength))
c
precision.combo$fRepeat<-as.factor(precision.combo$Repeat)
d<-ggplot(data=output.permanova.combo.temp,aes(x=total_distance,y=mean))+geom_point(aes(color=n))
d
```


```{r}
#Simple histogram of frequency distribution dissimilarity values per transect length
myhist2 = function(d,breaks) {
  n.nan = sum(is.nan(d))
  my.breaks = (0:breaks)/breaks
  v=hist(d, breaks = my.breaks,xlim=c(-0.1,1),las=1,
        main = "", xlab = "", ylab = "",ylim=c(0,40000))
  print(v)
  points(-0.075,n.nan,pch = 19,cex = 1)
  text(-0.075,0.0,"NaN",pos = 3)
  return(v$counts)
}
fish.mat.10<-Transformation_data(data.repeat.10,"4root")
fish.dist.10<-vegdist(fish.mat.10,method="bray")
myhist2(fish.dist.10,10)
fish.mat.20<-Transformation_data(data.repeat.20,"4root")
fish.dist.20<-vegdist(fish.mat.20,method="bray")
myhist2(fish.dist.20,10)
fish.mat.30<-Transformation_data(data.repeat.30,"4root")
fish.dist.30<-vegdist(fish.mat.30,method="bray")
myhist2(fish.dist.30,10)
fish.mat.40<-Transformation_data(data.repeat.40,"4root")
fish.dist.40<-vegdist(fish.mat.40,method="bray")
myhist2(fish.dist.40,10)
fish.mat.50<-Transformation_data(data.repeat.50,"4root")
fish.dist.50<-vegdist(fish.mat.50,method="bray")
myhist2(fish.dist.50,10)
```

```{r}
#Assessment between and within variability
#Within 1 Transect: Between (Persons)
list=unique(data.repeat.50$Code_Transect)
for (i in 1:length(list)){
  test<-data.repeat.50[which(data.repeat.50$Code_Transect==list[i]),]
  mean.ID <-as.data.frame(mean(test$totalamountofspecies)-tapply(test$totalamountofspecies, test$Person, mean))
  colnames(mean.ID)="var"
  mean.ID$type="between"
  within.ID <- as.data.frame(test$totalamountofspecies - rep(tapply(test$totalamountofspecies, test$Person, mean), rep(6,3)))
  colnames(within.ID)="var"
  within.ID$type="within"
  if (i==1){
    x=rbind(mean.ID,within.ID)
    x$Code_Transect<-list[i]
  }
  else {
    y=rbind(mean.ID,within.ID)
    y$Code_Transect<-list[i]
    x=rbind(x,y)
  }
}
g<-ggplot(data = x, aes(x=Code_Transect, y=var)) + geom_boxplot(aes(fill=type))
g
```

```{r}
#Assessment between and within variability
#Within 1 Person en 1 Location: Between (Transects)
data.repeat.50$Person_loc=paste(data.repeat.50$Person,data.repeat.50$Location,sep="_")
list=unique(data.repeat.50$Person_loc)
for (i in 1:length(list)){
  test<-data.repeat.50[which(data.repeat.50$Person_loc==list[i]),]
  mean.ID <-as.data.frame(mean(test$totalamountofspecies)-tapply(test$totalamountofspecies, test$Code_Transect, mean))
  colnames(mean.ID)="var"
  mean.ID$type="between"
  within.ID <- as.data.frame(test$totalamountofspecies - rep(tapply(test$totalamountofspecies, test$Code_Transect, mean), rep(6,3)))
  colnames(within.ID)="var"
  within.ID$type="within"
  if (i==1){
    x=rbind(mean.ID,within.ID)
    x$Person_loc<-list[i]
  }
  else {
    y=rbind(mean.ID,within.ID)
    y$Person_loc<-list[i]
    x=rbind(x,y)
  }
}
g<-ggplot(data = x, aes(x=Person_loc, y=var)) + geom_boxplot(aes(fill=type))
g
```

```{r}
#Assessment between and within variability
#Within 1 Location: Between Transects
list=unique(data.repeat.50$Location)
for (i in 1:length(list)){
  test<-data.repeat.50[which(data.repeat.50$Location==list[i]),]
  mean.ID <-as.data.frame(mean(test$totalamountofspecies)-tapply(test$totalamountofspecies, test$Code_Transect, mean))
  colnames(mean.ID)="var"
  mean.ID$type="between"
  within.ID <- as.data.frame(test$totalamountofspecies - rep(tapply(test$totalamountofspecies, test$Code_Transect, mean), rep(54,3)))
  colnames(within.ID)="var"
  within.ID$type="within"
  if (i==1){
    x=rbind(mean.ID,within.ID)
    x$Location<-list[i]
  }
  else {
    y=rbind(mean.ID,within.ID)
    y$Location<-list[i]
    x=rbind(x,y)
  }
}
g<-ggplot(data = x, aes(x=Location, y=var)) + geom_boxplot(aes(fill=type))
g
```
```{r}
#Assessment between and within variability
#Within 1 Location: Between Persons
list=unique(data.repeat.50$Location)
for (i in 1:length(list)){
  test<-data.repeat.50[which(data.repeat.50$Location==list[i]),]
  mean.ID <-as.data.frame(mean(test$totalamountofspecies)-tapply(test$totalamountofspecies, test$Person, mean))
  colnames(mean.ID)="var"
  mean.ID$type="between"
  within.ID <- as.data.frame(test$totalamountofspecies - rep(tapply(test$totalamountofspecies, test$Person, mean), rep(54,3)))
  colnames(within.ID)="var"
  within.ID$type="within"
  if (i==1){
    x=rbind(mean.ID,within.ID)
    x$Location<-list[i]
  }
  else {
    y=rbind(mean.ID,within.ID)
    y$Location<-list[i]
    x=rbind(x,y)
  }
}
g<-ggplot(data = x, aes(x=Location, y=var)) + geom_boxplot(aes(fill=type))
g
```

```{r}
#Assessment between and within variability
#Within 1 Island: Between Locations
list=unique(data.repeat.50$Island)
for (i in 1:length(list)){
  test<-data.repeat.50[which(data.repeat.50$Island==list[i]),]
  mean.ID <-as.data.frame(tapply(test$totalamountofspecies, test$Location, mean)-mean(test$totalamountofspecies))
  colnames(mean.ID)="var"
  mean.ID$type="between"
  within.ID <- as.data.frame(rep(tapply(test$totalamountofspecies, test$Location, mean), rep(270,5))-test$totalamountofspecies)
  colnames(within.ID)="var"
  within.ID$type="within"
  if (i==1){
    x=rbind(mean.ID,within.ID)
    x$Island<-list[i]
  }
  else {
    y=rbind(mean.ID,within.ID)
    y$Island<-list[i]
    x=rbind(x,y)
  }
}
g<-ggplot(data = x, aes(x=Island, y=var)) + geom_boxplot(aes(fill=type))
g
```

```{r}
#Assessment effect counting metric, resemblance matrix, transformation, transect length on level of unexplained variability
data.repeat.list.N=list(data.repeat.10,data.repeat.20,data.repeat.30,data.repeat.40,data.repeat.50)
data.repeat.list.maxN=list(data.repeat.10,data.repeat.20,data.repeat.30,data.repeat.40,data.repeat.50)
transform=c("presence-absence","4root","log")
method=c("bray","euclidean","kulczynski","gower")
TransectLength=c(10,20,30,40,50)
metric=c("N","maxN")
a<-expand.grid(TransectLength=TransectLength,metric=metric,transform=transform,method=method,stringsAsFactors = FALSE)
for (i in 1:nrow(a)){
  if (a$metric[i]=="maxN"){
    if (a$TransectLength[i]==10){
      data=data.repeat.10
    }
    if (a$TransectLength[i]==20){
      data=data.repeat.20
    }
    if (a$TransectLength[i]==30){
      data=data.repeat.30
    }
    if (a$TransectLength[i]==40){
      data=data.repeat.40
    }
    if (a$TransectLength[i]==50){
      data=data.repeat.50
    }
  }
  if (a$metric[i]=="N"){
    if (a$TransectLength[i]==10){
      data=data.repeat.10
    }
    if (a$TransectLength[i]==20){
      data=data.repeat.20
    }
    if (a$TransectLength[i]==30){
      data=data.repeat.30
    }
    if (a$TransectLength[i]==40){
      data=data.repeat.40
    }
    if (a$TransectLength[i]==50){
      data=data.repeat.50
    }
  }
  tryCatch({
  p<-Personal_PERMANOVA(data.repeat=data,
                     factors=c('Island','Location','Code_Transect','Person'),
                     response='fish.dist',
                     algo='*',
                     type="adonis",
                     transform=a$transform[i],
                     method=a$method[i]
                     )
  if (i==1){
    rownames=rownames(p$aov.tab)
    a[,rownames]<-NA
  }
  q<-p$aov.tab
  a[i,rownames]=q$R2
  },error=function(e){cat("ERROR :",conditionMessage(e), "\n")})
}
squaredR_for_different_combos<-a
```

```{r}
#Plot assessment effect counting metric, resemblance matrix, transformation, transect length on level of unexplained variability
general_theme<-theme(
                           axis.line = element_line(colour = "black"),
                           text=element_text(size=16,  family="serif"),
                           panel.background = element_rect(fill = "white", colour = NA),
                           panel.grid.major = element_line(colour = "gray"),
                           panel.grid.minor = element_blank(),
                           axis.title = element_text(size = rel(0.75), colour = "black"),
                           axis.text = element_text(size = rel(0.75), colour = "black"),
                           line = element_line(colour = "black", size = 0.5, linetype = 1, lineend = "butt")
                           )


a$fTransectLength<-as.factor(a$TransectLength)
a$metric[which(a$metric=="maxN")]="MinCount"
a$metric[which(a$metric=="N")]="MaxCount"
h<-ggplot(data=a,aes(x=fTransectLength,y=Residuals))+stat_boxplot(geom ='errorbar')+geom_boxplot()
h<-h+general_theme+ylab("R Residuals")+xlab("Transect length (m)")

h
i<-ggplot(data=a,aes(x=metric,y=Residuals))+stat_boxplot(geom ='errorbar')+geom_boxplot()
i<-i+general_theme+ylab("R Residuals")+xlab("Metric")
i
j<-ggplot(data=a,aes(x=transform,y=Residuals))+stat_boxplot(geom ='errorbar')+geom_boxplot()
j<-j+general_theme+ylab("R Residuals")+xlab("Transformation")
j
k<-ggplot(data=a,aes(x=method,y=Residuals))+stat_boxplot(geom ='errorbar')+geom_boxplot()
k<-k+general_theme+xlab("Dissimilarity matrix")+ylab("R Residuals")
k
```

```{r}
a$fTransectLength<-as.factor(a$TransectLength)
j<-ggplot(data=a,aes(x=metric,y=Residuals,color=fTransectLength))+stat_boxplot(geom ='errorbar')+geom_boxplot()
j<-j+general_theme+ylab("R? Residuals")+xlab("Transformation")
j
```


```{r}
#Assessment effect counting metric, resemblance matrix, transformation, transect length on level of explained variability
a$Total<-NULL
a <- a %>% 
  dplyr::rename(
    Observer = Person,
    Transect = Code_Transect,
    `Island:Observer`=`Island:Person`,
    `Location:Observer`=`Location:Person`,
    `Transect:Observer`=`Code_Transect:Person`
    )
b<-melt(a, id=c("TransectLength","metric","transform","method","fTransectLength"))
h<-ggplot(data=b,aes(x=fTransectLength,y=value,color=variable))+stat_boxplot(geom ='errorbar')+geom_boxplot()
h<-h+general_theme+ylab("R")+xlab("Transect length (m)")
h
i<-ggplot(data=b,aes(x=metric,y=value,color=variable))+stat_boxplot(geom ='errorbar')+geom_boxplot()
i<-i+general_theme+ylab("R")+xlab("Metric")
i
j<-ggplot(data=b,aes(x=transform,y=value,color=variable))+stat_boxplot(geom ='errorbar')+geom_boxplot()
j<-j+general_theme+ylab("R")+xlab("Transformation")
j
k<-ggplot(data=b,aes(x=method,y=value,color=variable))+stat_boxplot(geom ='errorbar')+geom_boxplot()
k<-k+general_theme+ylab("R")+xlab("Dissimilarity matrix")
k

```